### 2015-02-02 paper.tex
create a template for MCM

\documentclass[12pt,a4paper,titlepage]{article}
%\usepackage[doublespacing]{setspace}
\usepackage[utf8]{inputenc}         %This is used for ASKII digits.
\usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
\usepackage{amsfonts,mathrsfs}      %fonts~~
\usepackage{graphicx}               %This is for graph inserting.
\usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
%\usepackage{bm}                     %various kinds of bold texts.
\usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
\usepackage{indentfirst}            %Indent the first letter
\usepackage{fancyhdr}               %Below is the head of the article.
\pagestyle{fancy}
\usepackage{lastpage}
\lhead{Team \# 30061}
\rhead{Page \thepage{} of \pageref{LastPage}}
\cfoot{}
%\numberwithin{equation}{section}    %Numbering of the equations will be based on sections.
%\usepackage{amsthm}
%\theoremstyle{definition}
%\newtheorem{def}{Definition}  %Below set the theorem system.
%\theoremstyle{plain}
%\newtheorem{thm}[law]{Thm}
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
\usepackage{float}
\usepackage{paralist}
\usepackage{url}

\begin{document}

\title{}
\date{}
\maketitle

\tableofcontents

\newpage

\section{Introduction}
\label{sec:introduction}

\subsection{Restatement of the Problem}
\label{sec:restatement-of-the-problem}

\subsection{Literature Review}
\label{sec:literature-review}

\begin{itemize}
    \item
    \item
    \item
\end{itemize}

\section{Terminology}
\label{sec:terminology}

\begin{itemize}
    \item
    \item
    \item
\end{itemize}

\section{Assumptions and Justifications}
\label{sec:assumptions-and-justifications}

\begin{itemize}
    \item
    \item
    \item
\end{itemize}

%the main section of the paper
\section{}
\label{sec:}

%some other section of the paper
\section{}
\label{sec:}

\section{Performance and Analysis}
\label{sec:performance-and-analysis}

\subsection{General Performance}
\label{sec:general-performance}

\subsubsection*{Results and Analysis}

%some more specific results and analysis
\subsection{}
\label{sec:}

\subsubsection*{Results and Analysis}

\section{Sensitivity Analysis}
\label{sec:sensitivity-analysis}

%for some improvement of the problem
\section{}
\label{sec:}

\section{Strengths and Weaknesses}
\label{sec:strengths-and-weaknesses}

\subsection*{Strengths}
\label{sec:strengths}

\begin{itemize}
    \item
    \item
    \item
\end{itemize}

\subsection*{Weaknesses}
\label{sec:weaknesses}

\begin{itemize}
    \item
    \item
    \item
\end{itemize}

\section{Conclusions}
\label{sec:conclusions}

%the reference
\begin{thebibliography}{99}

\bibitem{}

\end{thebibliography}

\label{LastPage}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-02-09 paper.tex
Update paper

@@
 \usepackage{lastpage}
-\lhead{Team \# 30061}
+\lhead{Team \# 33131}
 \rhead{Page \thepage{} of \pageref{LastPage}}
@@
 
-\title{}
-\date{}
+\title{Human Capital Model} \date{\today{}}
 \maketitle
@@
 \label{sec:introduction}
+
+Considering the shortage of the talent, it's essential for companys to
+retain good people and make them well-trained. However, current
+situation is not satisfactory while many talents always tend to get a
+good job via job-hopping, causing orgnizational churn in employees who
+are closely connected to them. In order to simulate this process and
+improve it, we build a human capital model based on Social Network
+Analysis and Markov process.
 
@@
 \begin{itemize}
-    \item
-    \item
-    \item
+\item \textbf{assumption 1} If an employee has probability to
+  promote, he won't churn.
+
+The possibility of the unforeseen accidents, which could force an
+employee to leave his position,is neglected.Human nature, an employee
+will stay at his position to chase for higher level.
+
+\item \textbf{assumption 2} For a vacancy,if there exists an
+  employee measures up to it already,ICM won't recruit for it.
+
+Since recruiting good people is difficult, time consuming and
+expensive according to issue 5,it is wasteful to recruit for a
+position if an employee can promote to it.
+
+\item \textbf{assumption 3} Demotion won't occur.
+
+\item \textbf{assumption 4} Administrative clerk won't promote or be
+  transferred.
+
+\item \textbf{assumption 5} For the promotion probability and
+  organization change, the other factors effects the churn probability
+  is invariable.
+
+Though churn derives from varieties of reasons and they are actually
+lacking of known conditions and data to estimate them, we have to
+regard it as stable in our model.
+
+\item \textbf{assumption 6} Each division or office have at least one
+  middle manager or senior manager.
+
 \end{itemize}
 
-%the main section of the paper
-\section{}
-\label{sec:}
+% the main section of the paper
+\section{Human Capital Model}
+\label{sec:human-capital-model}
 
-%some other section of the paper
-\section{}
-\label{sec:}
+\subsection{Model Overview}
+\label{sec:model-overview}
+
+Most research for human capital can be classified as either
+microscopic and macroscopic. Since either macroscopic or microscopic
+methods are difficult to solve our problem perfectly, we approach the
+problem with the combination of macroscopic and microscopic methods.
+
+To measure the ability of each person, we use Quantitative Management
+Performance. Via this measurement, we can classify differient kinds of
+employees which will influence the promotion process.
+
+To build the employee network and analyze its properties, we employ
+the social network analysis (SNA) technique. In our case, the
+employees are viewed as nodes and relationships as links among
+them. So, We can simulate the complex relationship via this network.
+
+Definitions of symbols employed in this paper are listed in
+\textbf{Table 1}.
+\begin{table}
+\begin{tabular}{|l|l|}
+  Variable & Description \\
+  \hline
+  $i$            &Index of an employee \\
+  $L_{i,t}$          &The level of $i$ \\
+  $s_{ij,t}$        &The relation strength from $i$ to $j$ \\
+  $a_{ij,t}$        &Represent the influence caused by relationship
+                    between superior and subordinate \\
+  $f_{ij,t}$        &Represent the influence caused by relationship
+                    between person with many friends and person with
+                    few friends \\
+  $c_{i,t}$        &Clustering Coefficient of $i$
+\end{tabular}
+\end{table}
+
+\subsection{Human Performance Model}
+\label{sec:human-model}
+
+In this part, we buid a people model to evaluate an employee in four
+aspects, in terms of \textbf{Quantitative Management Performance} ---
+work achievement, work ability, work attitude and potential. These
+four aspects are supposed to be quantized according to annual
+evaluation based on performance as judged by the supervisor and we
+take these independent variables as $A_{ac_i}$, $A_{ab_1}$, $A_{at_i}$
+and $A_{po_i}$ for each employee $i$. For each of the four parameters,
+it goes from 0 to 1. The statues are used for calculating the
+probability that employee can promote. Meanwhile, they influence
+leaving probability and team cohesiveness as well.
+
+It is obvious that some of the parameters are somehow more important
+than others. So in an effort to make our model more accurate and
+reliable,we introduce a weighted index of deviation $AD_i$, with
+\begin{equation}
+  A_i=w_{ac} \cdot A_{ac_i} + w_{ab} \cdot A_{ab_i} + w_{at} \cdot A_{at_i} +
+  w_{po} \cdot A_{po_i}
+\end{equation}
+
+We determine weights via the Analytical Hierarchy Process(AHP) [Saaty
+1982]. We build a $4 \times 4$ reciprocal matrix by pair comparison:
+\begin{center}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+       &$A_{ac}$      &$A_{ab}$  &$A_{at}$    &$A_{po}$  \\ \hline
+ $A_{ac}$ & 1           & 5 & 2            &1            \\ \hline
+ $A_{ab}$ &$\frac{1}{5}$ & 1 &$\frac{1}{3}$ & $\frac{1}{4}$\\ \hline
+ $A_{at}$ &$\frac{1}{2}$ & 3 & 1            &1            \\ \hline
+ $A_{po}$ &1            & 4 & 1            &1            \\ \hline
+\end{tabular}
+\end{center}
+
+The meaning of the number in each cell is explained in []. The numbers
+themselves are based on our own subjective decisions.
+
+We then get the weight of each factor by calculating the bigest
+eigenvalue and it's corresponding eigenvector, as given in Table.
+
+\begin{center}
+\begin{tabular}{c|cccc}
+  Factor  &$A_{ac}$    &$A_{ab}$   &$A_{at}$    &$A_{po}$\\ \hline
+  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\
+\end{tabular}
+\end{center}
+
+We test the consistency of the preferences for this instance of the
+AHP. For good consistency [Alonso and Lamata 2006, 446 - 447]:
+
+\begin{itemize}
+\item The principal eigenvalue $\lambda_{max}$ of the matrix should be
+  close to the number n of alternatives, here 4; we get $\lambda_{max} = 4.047$.
+\item The consistency index $CI = (\lambda_{max}-n)/(n-1)$ should be close to 0; we get $CI = 0.0157$.
+\item The consistency ratio $CR = CI/RI$ (where RI is the average
+  value of CI for random matrices) should be less than 0.1; we get $CR
+  = 0.0182$.
+\end{itemize}
+
+Hence, our decision method displays perfectly acceptable consistency
+and the weights are reasonable.
+
+\subsection{Social Network Model}
+\label{sec:social-network-model}
+
+The social network model contains a directed weighted graph $G(V,E)$
+in which $V$ denote the employees and $E$ denote the connection
+between employees. Since there are personnel changes, $G(V,E)$ will
+change with time goes by. In order to simulate this situation, we use
+$G_t(V_t,E_t)$ instead of $G(V,E)$ where $t$ is a discrete
+variable. So $G_t(V_t,E_t)$ denote the social network in the $t$-th
+month.
+
+First, we explain the way we build edges of $G_t(V_t,E_t)$.
+
+When $t = 0$, there are about $370 \times 85\%$ nodes (employees) in
+$G_t$. We build edges between employees in the same division or
+office, since employees in the same division or office certainly know
+each other. So each division or office form a complete graph and
+employees in the differient division or office don't know others,
+which is impossible. To solve this problem, we build 10 edges for each
+employee with employees in other divisions with equal
+probability. Then we build the other edges with probability
+$p = \frac{\left|N_{i,t} \cap N_{j,t}\right|}{\left|N_{i,t} \cup
+    N_{j,t}\right|}$
+which is called Jaccard similarity coefficient[Jaccard 1901].
+
+When $t > 0$, there will be employees leaving or joining the
+company. If an employee leave, all his edges with other employees with
+be deleted. If an employee newly join the company, he will follow
+steps which employees at $t = 0$ take. This is the dynamic process of
+graph $G_t(V_t,E_t)$.
+
+Let $s_{ij,t}$ denote the weight from $i$ to $j$ at time $t$. We have
+these properties of $G_t(V_t,E_t)$:
+
+\begin{itemize}
+\item $s_{ij,t} \ne s_{ij,t}$
+
+  We made this graph directed and weighted because one person may
+  consider another person his best friend while that person doesn't
+  consider him a good friend. This situation may appear because of the
+  relationship between superior and subordinate and the relationship
+  between person with more friend and person with less friend. In
+  general, $s_{ij,t} \ne s_{ij,t}$ for the reason above.
+
+\item $s_{ij,t}=\dfrac{a_{ij,t}+f_{ij,t}}{2}$
+
+  $a_{ij,t}$ denote the influence caused by the relationship between
+  superior and subordinate, $f_{ij,t}$ denote the influence caused by
+  the amount of friends for $i$ and $j$. We define
+$$a_{ij,t}=\begin{cases}
+  \frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} \ge L_{j,t} \\
+  1-\frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} < L_{j,t} \\
+\end{cases}$$
+, where $L_{i,t}$ denote the level of $i$ at time $t$, and
+$$f_{ij,t}=\frac{\left|N_{i,t} \cap
+    N_{j,t}\right|}{\left|N_{i,t}\right|}$$.
+
+\end{itemize}
+
+Finally, we explain the concept of clustering coefficient [Duncan
+J. Watts and Steven Strogatz 1998] of $i$ denoted as $c_{i,t}$, which
+is a measure of the degree to which nodes in a graph tend to cluster
+together. $c_{i,t}$ is defined as:
+
+$$c_{i,t}=\dfrac{\left| \left\{ s_{jk,t}:v_j,v_k \in M_i,s_{jk,t} \in E
+    \right\} \right|}{k_{i,t}(k_{i,t}-1)}$$
+where
+$M_{i,t}=\left\{ v_j:s_{ij,t} \in E \and s_{ji,t} \in E \right\}$ and
+$k_{i,t}=\left| N_{i,t} \right|$.
+
+\subsection{Promote and Churn Model}
+\label{sec:promote-and-churn-model}
+
+The main part of our model is the algorithm which controls the
+behavior of employees. According to assumption 1 and assumption 2, we
+have the methodology as follow:
+
+\begin{itemize}
+\item [\textit{step 1}]
+\end{itemize}
+
+The network of the company we've built changes in terms of
+orgnizational churn and promotion. Considering various of factors in
+reality, we build an orgnizational churn and promotion model to
+predict the dynamic process.
+
+The first part of the model is churn model.We define the churn rate of
+an employee $i$ as $l_i$ to evaluate the probability to churn. $l_i$ is
+usually controlled by sorts of factors to different degrees. We
+divides $l_i$ into three parts:$l_{i1}$, $l_{i2}$ and$l_{i3}$.  $l_{i1}$
+represents the churn rate because of lacking of promotion
+opportunity. $l_{i2}$ represents the churn rate because of the changes
+of other employees related to employee $i$. To simplify our model, we
+presume that $l_i1$, $l_i2$ is linear correlated with $(1-p_i)$ and
+$s_i$, which means
+
+\begin{equation}
+  l_{i1}=\lambda_1(1-p_i),l_{i2}=\lambda_2s_i
+\end{equation}
+
+$\lambda_1$ and $\lambda_2$ could be ensured in later calculation.
+
+$l_{i3}$ represents the other factors we can't get any information from
+the known conditons so that we regard it as stable.  Thus
+
+\begin{equation}
+  l_i = \lambda_1(1-p_i) + \lambda_2s_i +l_i3
+\end{equation}
+
+After analyzing a great deal of churn rate reports, we get the
+composition of the three parts are 10.9\%, 2.2\% and 75.4\%
+respectively. According to the percentage and the general
+churn rate 18\%, we can calculate $\lambda_1$, $\lambda_2$ and
+$l_{i3}$. As an orinigal condition,it satisfies
+
+\begin{equation}
+\begin{cases}
+  \lambda_1 \sum_{i=1}^{370}(1-p_i)=10.9\% \times 370 \times 1.5\% \\
+  \lambda_2 \sum_{i=1}^{370}s_i=2.2\% \times 370 \times 1.5\% \\
+  l_i3=1.5 \% \times 75.4 \%
+\end{cases}
+\end{equation}
+
+Thus we can use equation (4) to calculate the churn rate $l_i$.
+
+The second part of the model is promotion model aimed to predict the
+promotion condition.We define the promotion rate of an employee i as
+$p_i$ to evaluate the probability to promote.As a matter of fact,if
+there is a vacancy, judging if an employee suits the site involves
+work experience and ability.It is essential that he is supposed to
+have several years of work experience according to issue 6.If an
+employee satisfies the experience condition,it turns out to think
+about his ability.Since in people model,each employee's ability is
+evaluated by a parameter $A_{D_i}$. For each level of position,it has
+an ability standard,as shows in Figure[]. The ability of an employee
+are supposed to reach the four standard parameters
+respectively,otherwise its $p_i$ is 0.For those who reach the
+standard, the promotion probability can be calculated by the equation:
+$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ is
+employee who have probability to promote.
 
@@
 
-\subsection{General Performance}
-\label{sec:general-performance}
+\subsection{Analysis for Task 2}
+\label{sec:analysis-for-task-2}
 
-\subsubsection*{Results and Analysis}
+a
 
-%some more specific results and analysis
-\subsection{}
-\label{sec:}
+\subsection{Analysis for Task 3}
+\label{sec:analysis-for-task-3}
 
-\subsubsection*{Results and Analysis}
+a
+
+\subsection{Analysis for Task 4}
+\label{sec:analysis-for-task-4}
+
+a
+
+\subsection{Analysis for Task 5}
+\label{sec:analysis-for-task-5}
+
+a
+
+\section{Advice for HR}
+\label{sec:advice-for-hr}
+
+a
+
+\subsection{Incentive Mechanism}
+\label{sec:incentive-machanism}
+
+a
+
+\subsection{Matching Employees to the Right Position}
+\label{sec:matching-employees-to-the-right-position}
+
+a
+
+\section{Team Science}
+\label{sec:team-science}
+
+a
 
@@
 
-%for some improvement of the problem
-\section{}
-\label{sec:}
+a
 
@@
 \begin{itemize}
-    \item
-    \item
-    \item
+\item Our model make fully use of the theory of multilayer networks so
+  that it quantizes the relation accurately and reasonablly.
+\item Our model exellently proves the interaction among these
+  factors:leave probability, promotion probability and productivity.
+\item The network we built include both microcosmic part and
+  macrocosmic part, and they react to each other.
+\item Our model proves the effection of time.
 \end{itemize}
@@
 \begin{itemize}
-    \item
-    \item
-    \item
+\item Limited by the time,we neglected sorts of factors which are not so significant.In fact, the model still has space to be perfected.
+\item The result has some randomness.
 \end{itemize}
@@
 
-%the reference
+a
+
+% the reference
 \begin{thebibliography}{99}

### 2015-02-09 paper.tex
Update paper

@@
 \pagestyle{fancy}
+\usepackage{booktabs}
 \usepackage{lastpage}
@@
 
-\subsection{Literature Review}
-\label{sec:literature-review}
+Problem C describe ICM as an orginaization of 370 people on human
+capital. The company is facing some issues. ICM tend to make a
+positive work atmosphere to gain the loyalty of an employee in their
+early time.The churn of an some employee makes effect on productivity
+and emotion on other employee. Lower quality employees often stay with
+the company for a full career. The churn rate is 18\% per year and
+mid-level positions suffer high  churn rate, even twice the average
+rate of the rest of the company. HR prefer matching employees to the
+right position. It only provides promotion opportunity for those who
+have several years of work experience. ICM usually has only 85\% of
+its 370 positions filled at any time and HR office is actively hiring
+about 8\%-10\% of the ICM positions. The CEO salary is approximately
+10 times the median of the salaries of all the employees, compared to
+hundreds of times the median as found in many companies.
+
+There are several tasks we need to finish according to our model:
 
 \begin{itemize}
-\item
-\item
-\item
-\end{itemize}
+\item Build a Human Capital network model of ICM organization’s
+  personnel situation.
 
-\section{Terminology}
-\label{sec:terminology}
+\item Identify dynamic processes within the Human Capital network,
+  which includes orginizatinal churn and direct and indirect effects on
+  the organization’s productivity.
 
-\begin{itemize}
-\item
-\item
-\item
+\item Analyze your organization’s budget requirements over the next 2
+  years.
+
+\item Judge if ICM could sustain its 80\% full status for positions if
+  the annual churn rate for all positions goes to 25\% and 35\%
+  respectively. Calculate the costs of these higher turnover rates and
+  describe the indirect effects of these high churn rates.
+
+\item Simulate the impact of 30\% churn in both junior managers and
+  experienced supervisors, if other churn values remain at 18\%.It
+  assumes that there is no external recruiting and ICM promote only
+  qualified employees for the next two years.
+
+\item Connect our Human Capital network to other organizational
+  network layers such as information flow, trust, influence, and
+  friendship that the other offices of ICM are considering building.
 \end{itemize}
@@
 evaluation based on performance as judged by the supervisor and we
-take these independent variables as $A_{ac_i}$, $A_{ab_1}$, $A_{at_i}$
+take these independent variables as $A_{ac_i}$, $A_{ab_i}$, $A_{at_i}$
 and $A_{po_i}$ for each employee $i$. For each of the four parameters,
@@
 
-The main part of our model is the algorithm which controls the
-behavior of employees. According to assumption 1 and assumption 2, we
-have the methodology as follow:
+First, we explain the model of promotion aimed to predict the
+promotion probability. We define the promotion rate of $i$ as
+$p_i$ to evaluate the probability to promote. As a matter of fact, if
+there is a vacancy, judging if an employee suits the site involves
+work experience and ability. It is essential that he is supposed to
+have several years of work experience according to issue 6. If an
+employee satisfies the experience condition, it turns out to think
+about his ability. Since in Human Performance Model, each employee's
+ability is evaluated by a parameter $A_{D_i}$. For each level of
+position, it has an ability standard, as shows in Table[]. The ability
+of an employee are supposed to reach the four standard parameters
+respectively, otherwise its $p_i$ is 0. For those who reach the
+standard, the promotion probability can be calculated by the equation:
+$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ represent
+employee who have probability to promote.
+
+According to assumption 1 and assumption 2, from $t$ to $t+1$, the
+model update once according to the following rules:
 
 \begin{itemize}
-\item [\textit{step 1}]
+\item [\textit{step 1}] Promotion: If there's a vacancy in superior
+  and $i$ has the ability to occupy this position, let $L_{i+1,t} =
+  L_{i,t}+1$ with probability mentioned above and build edges between
+  $i$ and his new colleagues.
+\item [\textit{step 2}] Churn: If $i$ isn't promoted, he will have the
+  probability to churn with a churn rate $l$.
+\item [\textit{step 3}] Stay: If $i$ hasn't been promoted or churned,
+  he will keep his job and do nothing.
 \end{itemize}
@@
 \begin{equation}
+\label{lambda}
 \begin{cases}
-  \lambda_1 \sum_{i=1}^{370}(1-p_i)=10.9\% \times 370 \times 1.5\% \\
-  \lambda_2 \sum_{i=1}^{370}s_i=2.2\% \times 370 \times 1.5\% \\
-  l_i3=1.5 \% \times 75.4 \%
+  \lambda_1 \sum_{i=1}^{370}(1-p_i) & =10.9\% \times 370 \times 1.5\% \\
+  \lambda_2 \sum_{i=1}^{370}s_i & =2.2\% \times 370 \times 1.5\% \\
+  l_{i3} & =1.5 \% \times 75.4 \%
 \end{cases}
@@
 
-Thus we can use equation (4) to calculate the churn rate $l_i$.
-
-The second part of the model is promotion model aimed to predict the
-promotion condition.We define the promotion rate of an employee i as
-$p_i$ to evaluate the probability to promote.As a matter of fact,if
-there is a vacancy, judging if an employee suits the site involves
-work experience and ability.It is essential that he is supposed to
-have several years of work experience according to issue 6.If an
-employee satisfies the experience condition,it turns out to think
-about his ability.Since in people model,each employee's ability is
-evaluated by a parameter $A_{D_i}$. For each level of position,it has
-an ability standard,as shows in Figure[]. The ability of an employee
-are supposed to reach the four standard parameters
-respectively,otherwise its $p_i$ is 0.For those who reach the
-standard, the promotion probability can be calculated by the equation:
-$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ is
-employee who have probability to promote.
+Thus we can use Equation\ref{lambda} to calculate the churn rate $l_i$.
 
@@
 \label{sec:analysis-for-task-5}
-
 a
@@
 
-a
+As the HR manager faces many problems such as identifying those that
+are likely to churn and maximizing employees' knowledge and
+abilities, we explain our further improved model.
 
@@
 
-a
+A worker is more likely to churn if he or she was connected to other
+former employees who have churned. So there are two kinds of people
+who should be highly paid attention to and incented.
+
+First, we should pay attention to those who have more friends than
+others. Because of their wide connection with other employees, the
+consequence of their churn may be destructive, which cause many
+friends' churn.
+
+Second, we focus on those having more friends who have churned
+during the past year. This kind of people have a great probability to
+churn because of the influence of others.
+
+We choose one sample in our simulations and 50 people in this sample
+to explain our incentive mechanism.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=7cm]{p1.eps}
+  \includegraphics[width=7cm]{p2.eps}
+  \caption{employees should be pay attention
+    to}\label{incentive-mechanism}
+\end{figure}
+
+In Figure\ref{incentive-mechanism}, as we can see, each vertex
+represents an employee, each full line represents a relation between 2
+employees, each imaginary line represent an relation between person
+who is on the job and person who churn. There are 5
+employees in left graph we should pay attention to which are
+43, 97, 123, 265 and 301 because they have more full lines than
+others. There are 6 employees in the right graph we should pay
+attention to which are 154, 175, 181, 182, 235 and 255 because they
+have more imaginary lines than others.
+
+We provide incentives to these employees which will decrease their
+probabilities to churn.
+
+At time $t$, we choose top 10\% of the employees which have the
+properties above and decrease their churn rate by 50\%. As shown in
+Figure\ref{}, the churn rate decrease rapidly.
 
@@
 
-a
+We consider different abilities of different employees. As we have an
+annual evaluation based on performance for each employee and each
+division or office has it's necessarily needed abilities, we can match
+employees with their most suitable position.
+
+Because the evaluation is given annually, we reassign employees
+annually according to their abilities and the formula below:
+
+\begin{equation}
+m_{i,j} =
+{(A_{ac_i}-B_{ac_j})}^2 + {(A_{ab_i}-B_{ab_j})}^2 + {(A_{at_i}-B_{at_j})}^2
++ {(A_{po_i}-B_{po_j})}^2
+\end{equation}
+
+where $B_{ac_j}$, $B_{ab_j}$, $B_{at_j}$, $B_{po_j}$ represent the
+abilities needed for position $j$.
+
+Defining $x_{ij}=\begin{cases} 1 , & \mbox{reassign employee } i
+  \mbox{ to position } j \\ 0,&\mbox{otherwise} \end{cases}$, we can
+describe this problem as a mathematical programming problem:
+
+\begin{equation}
+  \begin{split}
+  \min&\sum_{i=1}^n\sum_{j=1}^m m_{ij}x_{ij} \\
+  s.t.& \sum_{j=1}^m x_{ij}=1, i=1,2,\ldots,n \\
+  &\sum_{i=1}^n x_{ij} \le1,j=1,2,\ldots,m \\
+  &x_{ij}=0 \mbox{or} 1,i=1,2,\ldots,n,j=1,2,\ldots,m
+  \end{split}
+\end{equation}
+
+We can solve this problem via Kuhn–Munkres algorithm [Harold Kuhn and
+James Munkres 1957] whose time complexity is $O(n^4)$.
+
+We reassign them once a year according to their
+evaluation. Figure\ref{reassign} shows productivity with reassignment
+and without reassignment. We can find that the productivity increase
+rapidly after reassign employees, which means reassignment truly help
+with productivity of the company.
+
+\begin{figure}[center]
+  \centering
+
+  \caption{Productivity-Time Curve}\label{reassign}
+\end{figure}
 
@@
 
-a
+This part shows how our model connects to other organizational network
+layers such as information flow, trust, influence, and
+friendship. Number the layers from 0 to
+k. $$G^\alpha=(V^\alpha,E^\alpha), \alpha=1,2,\ldots,k$$ Each
+$E^\alpha$ is colored by a specific color. $G^0$ reprensents the
+network we built before, $G^1$, $G^2, \ldots ,G^k$ represent the other layers added.
+
+Still, in each network layer $G_\alpha$, $N_i$ represents emploee
+$i$. The edge $e_{ij}$ connects between two nodes $N_i$ and
+$N_j$. Each edge has a value $w_{ij}^\alpha$ proving the weight of
+edge $e_{ij}^\alpha$, positive correlated to the strength of
+connection between two employees in network layers $\alpha$. Then we
+connect these network layers together to built a general network
+$G_e=(V, E, C)$, V is node set, C is color set, $E\subst V\times
+V\times C$ is edge set. In the general model, different layers effects
+each other. Take for example, if the friendship between employee $i$
+and employee $j$ is deeper, with other conditions the same,their
+information flow is more fluent. $w_{ij}^\alpha$ is changing with time
+flows and G_e is a dynamic network.
+
+However, human capital network make the maily effect on other network
+layers. In the general network, if an empolyee churns or is
+reassigned, the edge related to him will change. That is,
+$w_{ij}^\alpha$ get a new value for all $\alpha$. Hence, human capital
+network takes the lead in this effort.
 
@@
 
-\bibitem{}
+\bibitem{} Huang Y. A Study of the Performance Assessment of State-owned Power Enterprisees[D]. Tianjing University, 2010.
+
+\bibitem{} Journal T E D O T. The Investigation Report of the Condition of employee churn in 2011[J]. China New Time, 2012(2).
+
+\bibitem{} Zhang J. The Empirical Research of the Factors effecting employee churn in Resource-oriented Enterprise in Yuncheng,Shandong [D]. Southerneast University, 2014.
+
+\bibitem{} MEJNewman. The Structure and Function of Complex Networks[D]. University of Michigan, 2003.
+
+\bibitem{} Fang J, Zheng Z, Bi Q, etal. A Brand-new
+  Interdisciplinary Science: Network Science (Part One)[J]. Progress in Physics, 2007, 27(3).
+
+\bibitem{} Fang J, Zheng Z, Bi Q, etal. A Brand-new
+  Interdisciplinary Science: Network Science (Part Two)[J]. Progress in Physics, 2007, 27(4).
 

### 2015-02-09 paper.tex
add analysis 3~5

--- 2015-02-09 paper.tex
@@
 \usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
+\usepackage{booktabs}
+\usepackage{caption2}
+\usepackage{epstopdf}
 \usepackage{amsfonts,mathrsfs}      %fonts~~
@@
 \newcommand{\boldit}[1]{\textbf{\textit{#1}}}
+\renewcommand{\captionlabelfont}{\small \bfseries \rmfamily}
 \usepackage{float}
@@
 
-a
+We assume that the company offers training programs for its employees monthly and newly hired employees start to get their salaries next month after they enter the company.
+With these two assumption, results can be drawn according to our model through simulation.
+
+Budget can be divided into threee parts: salary budget, training budget and recruiting budget. The budget requirement predicted for next two years is listed in the table below in terms of $\sigma$.
+
+\begin{tabular}{*{4}{c}}\toprule[2pt]
+Total Budget & Salary Budget & Training Budget & Recruiting Budget\\ \midrule
+1170.8$\sigma$ & 951.387$\sigma$ & 164.423$\sigma$ & 55.08$\sigma$ \\ \bottomrule[2pt]
+\end{tabular}
 
@@
 
-a
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=10cm]{task4_p.pdf}\\
+  \caption{Status of positions}\label{t4_p}
+\end{figure}
 
+To analyze the status of positions under different churn rate, we use our model to simulate dynamic processes with these churn rate constraints.
+We execute our program 100 times for each churn rate and average the predicted values.
+Figure \ref{t4_p} shows the averaged results our model predicted.
+Under all of these three conditions, the number of employees in the company keeps rising.
+The higher the churn rate, the lower the final full rate the company reaches after two years.
+But ICM can sustain its 80\% for positions even if the churn rate goes to 35\% according to our model's precition.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=10cm]{task4_r.pdf}\\
+  \caption{Recruiting budget}\label{t4_r}
+\end{figure}
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=7cm]{task4_t.pdf}
+  \includegraphics[width=7cm]{task4_s.pdf}\\
+  \caption{Training budget and salary budget}\label{t4_t_s}
+\end{figure}
+The churn rate effect the budget of the company as well.
+The three parts of the bugdet behave differently when churn rate increases.
+The calculated budget is shown in Figure \ref{t4_r} and Figure \ref{t4_t_s}.
+Each data point in three charts is an averaged result of 10 predictions and a linear trendline is added to each chart.
+It is clear that recruiting budget showed in Figure \ref{t4_r} is likely to be proportional to the churn rate while salary budget and training budget showed in Figure \ref{t4_t_s} are likely to be inversely proportional to the churn rate.
+
+To maintain enough employees, the company has to spend more on recruiting.
+So high turnover rate directly increase the recruiting budget.
+High turnover rate's effect on training budget and salary budget is more complex.
+On the one hand, when churn rate goes up, vacancies in the middle level keeps rising due to long recruiting time and low promote rate.
+On the other hand, the vacancies in lower level remains low because of the short recruiting time.
+So the full rate of the company decreases when churn rate rises.
+Since training budget and salary budget are closely related to full rate, both of them decrease when turnover rate goes up.
 \subsection{Analysis for Task 5}
@@
 
-a
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=10cm]{task5_p.pdf}\\
+  \caption{Status of position}\label{t5_p}
+\end{figure}
+We apply following changes to our model to simulate the required process:\\
+\begin{itemize}
+\item Change the churn rate of junior managers and experienced supervisors to 30\%
+\item Prohit external recruiting
+\item Promoting only qualified employees
+\end{itemize}
+\begin{table}
+	\begin{center}
+		\begin{tabular}{l|cc}\toprule[2pt]
+		\bfseries Level of Position & \bfseries Modified & \bfseries Original\\ \midrule
+		Senior manager/Executive & 5.6 & 8.4\\
+		Junior manager/Executive & 9.0 & 18.4\\
+		Experienced supervisor & 7.4 & 23.0\\
+		Inexperienced supervisor & 9.2 & 23.2\\
+		Experienced employee & 72.6 & 107.4\\
+		Inexperienced employee & 99.6 & 149.6\\
+		Administrative clerk & 24.0 & 24.0\\ \bottomrule[2pt]
+		\end{tabular}
+		\caption{Status of position}\label{t5_p_t}
+	\end{center}
+\end{table}
+
+The result of simulation is shown in Figure \ref{t5_p} and Table \ref{t5_p_t}.
+All the data shown is an average of ten predictions.
+While the number of positions occupied remains stable with origial conditions, it drops remarkably with modified conditions.
+
+We list specific data of each level in Table \ref{t5_p_t}.
+In the modified case, the numbers of employees are lower than original case especially the those of middle levels.
+Since there is no external recruiting in modified case, it is obivious that the full rate will decrease due to employees' leave.
+Although some qualified employees can be promoted into higher level, the high churn rate of the middle level and difficulty of satisfying the promotion conditions make the numbers of middle level employees relatively low.
+The situation given in that task 5 will cause unrecoverable damage to ICM's HR health.
+With the full rate of middle level employees lower than 50\%, the HR structure is broken into fragments and the company won't be able to function normally.
 

### 2015-02-09 paper.tex
Update paper

--- 2015-02-09 paper.tex
@@
 properties above and decrease their churn rate by 50\%. As shown in
-Figure\ref{}, the churn rate decrease rapidly.
+Figure\ref{churn-rate}, the churn rate decrease rapidly.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=11cm]{p4.pdf}
+  \caption{Churn rate-Time Curve}
+  \label{churn-rate}
+\end{figure}
 
@@
   &\sum_{i=1}^n x_{ij} \le1,j=1,2,\ldots,m \\
-  &x_{ij}=0 \mbox{or} 1,i=1,2,\ldots,n,j=1,2,\ldots,m
+  &x_{ij}=0 \mbox{ or } 1,i=1,2,\ldots,n,j=1,2,\ldots,m
   \end{split}
@@
 
-\begin{figure}[center]
+\begin{figure}[htb]
   \centering
-
+  \includegraphics[width=11cm]{p3.pdf}
   \caption{Productivity-Time Curve}\label{reassign}
@@
 $E^\alpha$ is colored by a specific color. $G^0$ reprensents the
-network we built before, $G^1$, $G^2, \ldots ,G^k$ represent the other layers added.
+network we built before, $G^1, G^2, \ldots ,G^k$ represent the other layers added.
 

### 2015-02-09 paper.tex

@@
 
-a
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=10cm]{task4_p.pdf}\\
+  \caption{Status of positions}\label{t4_p}
+\end{figure}
 
+To analyze the status of positions under different churn rate, we use our model to simulate dynamic processes with these churn rate constraints.
+We execute our program 100 times for each churn rate and average the predicted values.
+Figure \ref{t4_p} shows the averaged results our model predicted.
+Under all of these three conditions, the number of employees in the company keeps rising.
+The higher the churn rate, the lower the final full rate the company reaches after two years.
+But ICM can sustain its 80\% for positions even if the churn rate goes to 35\% according to our model's precition.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=10cm]{task4_r.pdf}\\
+  \caption{Recruiting budget}\label{t4_r}
+\end{figure}
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=7cm]{task4_t.pdf}
+  \includegraphics[width=7cm]{task4_s.pdf}\\
+  \caption{Training budget and salary budget}\label{t4_t_s}
+\end{figure}
+The churn rate effect the budget of the company as well.
+The three parts of the bugdet behave differently when churn rate increases.
+The calculated budget is shown in Figure \ref{t4_r} and Figure \ref{t4_t_s}.
+Each data point in three charts is an averaged result of 10 predictions and a linear trendline is added to each chart.
+It is clear that recruiting budget showed in Figure \ref{t4_r} is likely to be proportional to the churn rate while salary budget and training budget showed in Figure \ref{t4_t_s} are likely to be inversely proportional to the churn rate.
+
+To maintain enough employees, the company has to spend more on recruiting.
+So high turnover rate directly increase the recruiting budget.
+High turnover rate's effect on training budget and salary budget is more complex.
+On the one hand, when churn rate goes up, vacancies in the middle level keeps rising due to long recruiting time and low promote rate.
+On the other hand, the vacancies in lower level remains low because of the short recruiting time.
+So the full rate of the company decreases when churn rate rises.
+Since training budget and salary budget are closely related to full rate, both of them decrease when turnover rate goes up.
 \subsection{Analysis for Task 5}
 \label{sec:analysis-for-task-5}
-a
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=10cm]{task5_p.pdf}\\
+  \caption{Status of position}\label{t5_p}
+\end{figure}
+We apply following changes to our model to simulate the required process:\\
+\begin{itemize}
+\item Change the churn rate of junior managers and experienced supervisors to 30\%
+\item Prohit external recruiting
+\item Promoting only qualified employees
+\end{itemize}
+\begin{table}
+        \begin{center}
+                \begin{tabular}{l|cc}\toprule[2pt]
+                \bfseries Level of Position & \bfseries Modified & \bfseries Original\\ \midrule
+                Senior manager/Executive & 5.6 & 8.4\\
+                Junior manager/Executive & 9.0 & 18.4\\
+                Experienced supervisor & 7.4 & 23.0\\
+                Inexperienced supervisor & 9.2 & 23.2\\
+                Experienced employee & 72.6 & 107.4\\
+                Inexperienced employee & 99.6 & 149.6\\
+                Administrative clerk & 24.0 & 24.0\\ \bottomrule[2pt]
+                \end{tabular}
+                \caption{Status of position}\label{t5_p_t}
+        \end{center}
+\end{table}
+
+The result of simulation is shown in Figure \ref{t5_p} and Table \ref{t5_p_t}.
+All the data shown is an average of ten predictions.
+While the number of positions occupied remains stable with origial conditions, it drops remarkably with modified conditions.
+
+We list specific data of each level in Table \ref{t5_p_t}.
+In the modified case, the numbers of employees are lower than original case especially the those of middle levels.
+Since there is no external recruiting in modified case, it is obivious that the full rate will decrease due to employees' leave.
+Although some qualified employees can be promoted into higher level, the high churn rate of the middle level and difficulty of satisfying the promotion conditions make the numbers of middle level employees relatively low.
+The situation given in that task 5 will cause unrecoverable damage to ICM's HR health.
+With the full rate of middle level employees lower than 50\%, the HR structure is broken into fragments and the company won't be able to function normally.
 

### 2015-02-09 paper.tex
change environment

@@
 \usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
-%\usepackage{bm}                     %various kinds of bold texts.
+%\usepackage{bm}
+\usepackage{caption2}                 %various kinds of bold texts.
 \usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
@@
 
-\section{Assumptions and Justifications}
+% the main section of the paper
+\section{Human Capital Model}
+\label{sec:human-capital-model}
+
+\subsection{Assumptions and Justifications}
 \label{sec:assumptions-and-justifications}
@@
 The possibility of the unforeseen accidents, which could force an
-employee to leave his position,is neglected.Human nature, an employee
-will stay at his position to chase for higher level.
+employee to leave his position, is neglected. Based on human nature,
+an employee will stay at his position to chase for higher level.
 
 \item \textbf{assumption 2} For a vacancy,if there exists an
-  employee measures up to it already,ICM won't recruit for it.
+  employee measures up to it already, ICM won't recruit for it.
 
 Since recruiting good people is difficult, time consuming and
-expensive according to issue 5,it is wasteful to recruit for a
+expensive according to issue 5, it is wasteful to recruit for a
 position if an employee can promote to it.
@@
 
-\item \textbf{assumption 5} For the promotion probability and
-  organization change, the other factors effects the churn probability
-  is invariable.
-
-Though churn derives from varieties of reasons and they are actually
-lacking of known conditions and data to estimate them, we have to
-regard it as stable in our model.
-
-\item \textbf{assumption 6} Each division or office have at least one
+\item \textbf{assumption 5} Each division or office have at least one
   middle manager or senior manager.
@@
 \end{itemize}
-
-% the main section of the paper
-\section{Human Capital Model}
-\label{sec:human-capital-model}
 
@@
 
-Definitions of symbols employed in this paper are listed in
-\textbf{Table 1}.
+Definitions of symbols employed in this section are listed in Table
+\ref{variable1}:
 \begin{table}
-\begin{tabular}{|l|l|}
+  \centering
+  \begin{tabular}{l p{10cm}}
+  \toprule{}
   Variable & Description \\
-  \hline
+  \midrule{}
   $i$            &Index of an employee \\
@@
                     few friends \\
-  $c_{i,t}$        &Clustering Coefficient of $i$
+  $c_{i,t}$        &Clustering Coefficient of $i$ \\ \bottomrule{}
 \end{tabular}
+\caption{Variables and Descriptions}\label{variable1}
 \end{table}
@@
 
-The meaning of the number in each cell is explained in []. The numbers
-themselves are based on our own subjective decisions.
+The meaning of the number in each cell is explained in Figure
+\ref{important}. The numbers themselves are based on our own
+subjective decisions.
+
+\begin{table}[htb]
+  \centering
+  \begin{tabular}{cl}
+    \toprule{}
+    Intensity of Importance&Definition \\ \midrule{}
+    1                      &Equal Importance \\
+    2                      &Weak or slight \\
+    3                      &Moderate importance \\
+    4                      &Moderate plus \\
+    5                      &Strong importance \\
+    6                      &Strong plus \\
+    7                      &Very strong or demonstrated importance \\
+    8                      &Very, Very strong \\
+    9                      &Extreme importance \\ \bottomrule{}
+  \end{tabular}
+  \caption{The fundamental scale of absolute numbers}\label{important}
+\end{table}
 
 We then get the weight of each factor by calculating the bigest
-eigenvalue and it's corresponding eigenvector, as given in Table.
+eigenvalue and it's corresponding eigenvector, as given in Table \ref{weight}.
 
+\begin{table}
 \begin{center}
-\begin{tabular}{c|cccc}
-  Factor  &$A_{ac}$    &$A_{ab}$   &$A_{at}$    &$A_{po}$\\ \hline
-  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\
+\begin{tabular}{ccccc} \toprule{}
+  Factor  &$A_{ac}$    &$A_{ab}$   &$A_{at}$    &$A_{po}$\\ \midrule{}
+  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\ \bottomrule{}
 \end{tabular}
 \end{center}
+\caption{Weight for factors}\label{weight}
+\end{table}
 
 We test the consistency of the preferences for this instance of the
-AHP. For good consistency [Alonso and Lamata 2006, 446 - 447]:
+AHP.\@ For good consistency [Alonso and Lamata 2006, 446 - 447]:
 
@@
 
-Finally, we explain the concept of clustering coefficient [Duncan
-J. Watts and Steven Strogatz 1998] of $i$ denoted as $c_{i,t}$, which
-is a measure of the degree to which nodes in a graph tend to cluster
-together. $c_{i,t}$ is defined as:
-
-$$c_{i,t}=\dfrac{\left| \left\{ s_{jk,t}:v_j,v_k \in M_i,s_{jk,t} \in E
-    \right\} \right|}{k_{i,t}(k_{i,t}-1)}$$
-where
-$M_{i,t}=\left\{ v_j:s_{ij,t} \in E \and s_{ji,t} \in E \right\}$ and
-$k_{i,t}=\left| N_{i,t} \right|$.
-
 \subsection{Promote and Churn Model}
@@
   he will keep his job and do nothing.
+\item [\textit{step 4}] Recruit: Recruit for vacancies when all the
+  employees have done these 3 steps above.
 \end{itemize}
+
+\section{The Improved Model}
+\label{sec:the-improved-model}
+
+\subsection{Assumptions and Justifications}
+
+\begin{itemize}
+\item \textbf{assumption 1} For the promotion probability and
+  organization change, the other factors effects the churn probability
+  is invariable.
+
+Though churn derives from varieties of reasons and they are actually
+lacking of known conditions and data to estimate them, we have to
+regard it as stable in our model.
+\end{itemize}
+
+\subsection{Organizational Churn}
 
@@
 
+\subsection{Productivity}
+
+First, we explain the concept of clustering coefficient [Duncan
+J. Watts and Steven Strogatz 1998] of $i$ denoted as $c_{i,t}$, which
+is a measure of the degree to which nodes in a graph tend to cluster
+together. $c_{i,t}$ is defined as:
+
+$$c_{i,t}=\dfrac{\left| \left\{ s_{jk,t}:v_j,v_k \in M_i,s_{jk,t} \in E
+    \right\} \right|}{k_{i,t}(k_{i,t}-1)}$$
+where
+$M_{i,t}=\left\{ v_j:s_{ij,t} \in E \and s_{ji,t} \in E \right\}$ and
+$k_{i,t}=\left| N_{i,t} \right|$.
+
 \section{Performance and Analysis}
 \label{sec:performance-and-analysis}
-
-\subsection{Analysis for Task 2}
-\label{sec:analysis-for-task-2}
-
-a
 
@@
 
-To analyze the status of positions under different churn rate, we use our model to simulate dynamic processes with these churn rate constraints.
-We execute our program 100 times for each churn rate and average the predicted values.
-Figure \ref{t4_p} shows the averaged results our model predicted.
-Under all of these three conditions, the number of employees in the company keeps rising.
-The higher the churn rate, the lower the final full rate the company reaches after two years.
-But ICM can sustain its 80\% for positions even if the churn rate goes to 35\% according to our model's precition.
+To analyze the status of positions under different churn rate, we use
+our model to simulate dynamic processes with these churn rate
+constraints. We execute our program 100 times for each churn rate and
+average the predicted values. Figure \ref{t4_p} shows the averaged
+results our model predicted. Under all of these three conditions, the
+number of employees in the company keeps rising. The higher the churn
+rate, the lower the final full rate the company reaches after two
+years. But ICM can sustain its 80\% for positions even if the churn
+rate goes to 35\% according to our model's precition.
 
@@
 \end{figure}
-The churn rate effect the budget of the company as well.
-The three parts of the bugdet behave differently when churn rate increases.
-The calculated budget is shown in Figure \ref{t4_r} and Figure \ref{t4_t_s}.
-Each data point in three charts is an averaged result of 10 predictions and a linear trendline is added to each chart.
-It is clear that recruiting budget showed in Figure \ref{t4_r} is likely to be proportional to the churn rate while salary budget and training budget showed in Figure \ref{t4_t_s} are likely to be inversely proportional to the churn rate.
+The churn rate effect the budget of the company as well. The three
+parts of the bugdet behave differently when churn rate increases. The
+calculated budget is shown in Figure \ref{t4_r} and Figure
+\ref{t4_t_s}. Each data point in three charts is an averaged result of
+10 predictions and a linear trendline is added to each chart. It is
+clear that recruiting budget showed in Figure \ref{t4_r} is likely to
+be proportional to the churn rate while salary budget and training
+budget showed in Figure \ref{t4_t_s} are likely to be inversely
+proportional to the churn rate.
 
-To maintain enough employees, the company has to spend more on recruiting.
-So high turnover rate directly increase the recruiting budget.
-High turnover rate's effect on training budget and salary budget is more complex.
-On the one hand, when churn rate goes up, vacancies in the middle level keeps rising due to long recruiting time and low promote rate.
-On the other hand, the vacancies in lower level remains low because of the short recruiting time.
-So the full rate of the company decreases when churn rate rises.
-Since training budget and salary budget are closely related to full rate, both of them decrease when turnover rate goes up.
+To maintain enough employees, the company has to spend more on
+recruiting. So high turnover rate directly increase the recruiting
+budget. High turnover rate's effect on training budget and salary
+budget is more complex. On the one hand, when churn rate goes up,
+vacancies in the middle level keeps rising due to long recruiting time
+and low promote rate. On the other hand, the vacancies in lower level
+remains low because of the short recruiting time. So the full rate of
+the company decreases when churn rate rises. Since training budget and
+salary budget are closely related to full rate, both of them decrease
+when turnover rate goes up.
+
 \subsection{Analysis for Task 5}
@@
 
-The result of simulation is shown in Figure \ref{t5_p} and Table \ref{t5_p_t}.
-All the data shown is an average of ten predictions.
-While the number of positions occupied remains stable with origial conditions, it drops remarkably with modified conditions.
+The result of simulation is shown in Figure \ref{t5_p} and Table
+\ref{t5_p_t}. All the data shown is an average of ten
+predictions. While the number of positions occupied remains stable
+with origial conditions, it drops remarkably with modified
+conditions.
 
-We list specific data of each level in Table \ref{t5_p_t}.
-In the modified case, the numbers of employees are lower than original case especially the those of middle levels.
-Since there is no external recruiting in modified case, it is obivious that the full rate will decrease due to employees' leave.
-Although some qualified employees can be promoted into higher level, the high churn rate of the middle level and difficulty of satisfying the promotion conditions make the numbers of middle level employees relatively low.
-The situation given in that task 5 will cause unrecoverable damage to ICM's HR health.
-With the full rate of middle level employees lower than 50\%, the HR structure is broken into fragments and the company won't be able to function normally.
+We list specific data of each level in Table \ref{t5_p_t}. In the
+modified case, the numbers of employees are lower than original case
+especially the those of middle levels. Since there is no external
+recruiting in modified case, it is obivious that the full rate will
+decrease due to employees' leave. Although some qualified employees
+can be promoted into higher level, the high churn rate of the middle
+level and difficulty of satisfying the promotion conditions make the
+numbers of middle level employees relatively low. The situation given
+in that task 5 will cause unrecoverable damage to ICM's HR
+health. With the full rate of middle level employees lower than 50\%,
+the HR structure is broken into fragments and the company won't be
+able to function normally.
 

### 2015-02-09 paper.tex
Update paper

@@
 
+Analyzing the consequence of this phenomenon, we use our program to
+simulate this process. As a result, we find a organizational churn in
+our simulation as shown in Figure \ref{organizational-churn}.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=4cm]{Pic3_0.png}
+  \includegraphics[width=4cm]{Pic3_1.png}
+  \includegraphics[width=4cm]{Pic3_2.png}
+  \includegraphics[width=4cm]{Pic3_3.png}
+  \includegraphics[width=4cm]{Pic3_4.png}
+  \caption{Organizational Churn}\label{organizational-churn}
+\end{figure}
+
+The black spots in the graph denote employees who have churned
+
 \subsection{Productivity}
@@
   \centering
-  \includegraphics[width=11cm]{p4.pdf}
+ % \includegraphics[width=11cm]{p4.pdf}
   \caption{Churn rate-Time Curve}
@@
 connect these network layers together to built a general network
-$G_e=(V, E, C)$, V is node set, C is color set, $E\subst V\times
+$G_e=(V, E, C)$, V is node set, C is color set, $E \subset  V\times
 V\times C$ is edge set. In the general model, different layers effects
@@
 information flow is more fluent. $w_{ij}^\alpha$ is changing with time
-flows and G_e is a dynamic network.
+flows and $G_e$ is a dynamic network.
 

### 2015-02-09 paper.tex
finish

@@
 \usepackage{booktabs}
+\usepackage{makecell}
 \usepackage{lastpage}
@@
 
-\title{Human Capital Model} \date{\today{}}
+\title{Integrated Management Model for Human Capital}
+\date{}
 \maketitle
@@
 good job via job-hopping, causing orgnizational churn in employees who
-are closely connected to them. In order to simulate this process and
-improve it, we build a human capital model based on Social Network
+are closely connected to them.
+
+ICM is facing such an issue that the churn rate reachs 18\%.
+The churn rate of middle managers even reaches twice as much as others.
+At present, the company only has 85\% of its positions occupied while HR is recruiting only 8\%-10\% of the vacancies due to limited resources.
+In addition, HR department hopes to place employees to suitable positions to maximize their talent.
+In order to simulate this situation and help to improve it, we build a human capital model based on Social Network
 Analysis and Markov process.
 
-\subsection{Restatement of the Problem}
-\label{sec:restatement-of-the-problem}
-
-Problem C describe ICM as an orginaization of 370 people on human
-capital. The company is facing some issues. ICM tend to make a
-positive work atmosphere to gain the loyalty of an employee in their
-early time.The churn of an some employee makes effect on productivity
-and emotion on other employee. Lower quality employees often stay with
-the company for a full career. The churn rate is 18\% per year and
-mid-level positions suffer high  churn rate, even twice the average
-rate of the rest of the company. HR prefer matching employees to the
-right position. It only provides promotion opportunity for those who
-have several years of work experience. ICM usually has only 85\% of
-its 370 positions filled at any time and HR office is actively hiring
-about 8\%-10\% of the ICM positions. The CEO salary is approximately
-10 times the median of the salaries of all the employees, compared to
-hundreds of times the median as found in many companies.
-
-There are several tasks we need to finish according to our model:
+There are several tasks we need to accomplish:
 
 \begin{itemize}
-\item Build a Human Capital network model of ICM organization’s
-  personnel situation.
+\item Build a Human Capital network model of ICM's personnel situation.
 
 \item Identify dynamic processes within the Human Capital network,
-  which includes orginizatinal churn and direct and indirect effects on
-  the organization’s productivity.
+  which includes organizatinal churn and direct and indirect effects on
+  the organization's productivity.
 
-\item Analyze your organization’s budget requirements over the next 2
+\item Analyze the organization's budget requirements over the next 2
   years.
@@
 
-\item Simulate the impact of 30\% churn in both junior managers and
-  experienced supervisors, if other churn values remain at 18\%.It
-  assumes that there is no external recruiting and ICM promote only
-  qualified employees for the next two years.
+\item Assumes that there is no external recruiting and ICM promotes
+  only qualified employees for the next two years. Simulate the impact
+  of 30\% churn rate in both junior managers and experienced
+  supervisors, if other churn values remain 18\%.
 
@@
 \end{itemize}
+\section{Variables and Descriptions}
+
+Definitions of symbols employed in this section are listed in \textbf{Table
+\ref{variable1}}, where all the subscripts with $t$ represent the
+$t$-th month and all the subscripts with $i$ represent the employee
+indexed by $i$:
+
+\begin{table}
+  \centering
+  \begin{tabular}{l p{10cm}}
+  \toprule[2pt]
+  Variable & Description \\
+  \midrule{}
+  $i$            &Index of an employee \\
+  $L_{i,t}$          &The level of $i$ \\
+  $A_{ac_i,t}$       &The work achievement of $i$ \\
+  $A_{ab_i,t}$         &The work ability of $i$ \\
+  $A_{at_i,t}$        &The work attitude of $i$ \\
+  $A_{po_i,t}$       &The potential of $i$ \\
+  $A_{i,t}$          &The grade of $i$ \\
+  $s_{ij,t}$        &The relation strength from $i$ to $j$ \\
+  $a_{ij,t}$        &The influence caused by leader-member relation
+                    between $i$ and $j$ \\
+  $f_{ij,t}$        &The influence caused by friendship
+                    between $i$ and $j$\\
+  $c_{i,t}$        &The Clustering Coefficient of $i$ \\
+  $p_{i,t}$           &Promotion probability of $i$\\
+  $l_{i,t}$          &Churn probability of $i$ \\
+  $prod_{i,t}$       &Productivity of $i$ \\
+  $salary_{i,t}$     &Salary of $i$ \\
+  $d_{i,t}$          &The work experience of $i$ \\
+  $m_{ij}$           &The variable to reflect whether employee indexed
+                       by $i$ is suitable for position indexed by $j$
+                       \\
+  $B_{ac_j}$       &The suitable work achievement of position indexed
+                     by  $j$ \\
+  $B_{ab_j}$       &The suitable work ability of position indexed by
+                     $j$ \\
+  $B_{at_j}$       &The suitable work attitude of position indexed by
+                     $j$ \\
+  $B_{po_j}$       &The suitable potential of position indexed by $j$
+                     \\
+  $N$ & The number of employees over the next two years \\
+$p$ & The average productivity over the next two years \\
+$r$ & The percentage of recruiting positions in ICM positions \\
+$c$ & The current churn rate \\
+$ra$ & The ratio of the churn rate between middle managers and the
+       rest employees \\
+  \bottomrule[2pt]
+\end{tabular}
+\caption{Variables and Descriptions}\label{variable1}
+\end{table}
 
@@
 \begin{itemize}
-\item \textbf{assumption 1} If an employee has probability to
-  promote, he won't churn.
+\item \textbf{Assumption 1} If an employee has an opportunity to be promoted, he won't leave the company.
 
@@
 
-\item \textbf{assumption 2} For a vacancy,if there exists an
-  employee measures up to it already, ICM won't recruit for it.
+\item \textbf{Assumption 2} For each vacancy, if there exists an
+  employee satisfying its requirement, ICM won't recruit for it.
 
 Since recruiting good people is difficult, time consuming and
-expensive according to issue 5, it is wasteful to recruit for a
-position if an employee can promote to it.
+expensive, it is wasteful to recruit for a
+position if an employee satisfies the requirement.
 
-\item \textbf{assumption 3} Demotion won't occur.
+\item \textbf{Assumption 3} Demotion won't occur.
 
-\item \textbf{assumption 4} Administrative clerk won't promote or be
-  transferred.
+\item \textbf{Assumption 4} Administrative clerk won't be promoted or be
+  reassigned.
 
-\item \textbf{assumption 5} Each division or office have at least one
+\item \textbf{Assumption 5} Each division or office has at least one
   middle manager or senior manager.
@@
 
-Most research for human capital can be classified as either
-microscopic and macroscopic. Since either macroscopic or microscopic
-methods are difficult to solve our problem perfectly, we approach the
+Most researches on human capital can be classified as either
+microscopic or macroscopic. Since both macroscopic and microscopic
+methods alone can not solve the problem perfectly, we approach the
 problem with the combination of macroscopic and microscopic methods.
@@
 To measure the ability of each person, we use Quantitative Management
-Performance. Via this measurement, we can classify differient kinds of
+Performance. Via this measurement, we can classify different kinds of
 employees which will influence the promotion process.
@@
 To build the employee network and analyze its properties, we employ
-the social network analysis (SNA) technique. In our case, the
-employees are viewed as nodes and relationships as links among
-them. So, We can simulate the complex relationship via this network.
+the social network analysis (SNA) technique. In our model,
+ employees are viewed as nodes and relationships are viewed as links 
+ among employees. With this network, we can simulate the complex relationship.
 
-Definitions of symbols employed in this section are listed in Table
-\ref{variable1}:
-\begin{table}
-  \centering
-  \begin{tabular}{l p{10cm}}
-  \toprule{}
-  Variable & Description \\
-  \midrule{}
-  $i$            &Index of an employee \\
-  $L_{i,t}$          &The level of $i$ \\
-  $s_{ij,t}$        &The relation strength from $i$ to $j$ \\
-  $a_{ij,t}$        &Represent the influence caused by relationship
-                    between superior and subordinate \\
-  $f_{ij,t}$        &Represent the influence caused by relationship
-                    between person with many friends and person with
-                    few friends \\
-  $c_{i,t}$        &Clustering Coefficient of $i$ \\ \bottomrule{}
-\end{tabular}
-\caption{Variables and Descriptions}\label{variable1}
-\end{table}
-
-\subsection{Human Performance Model}
+\subsection{Employee Performance Model}
 \label{sec:human-model}
 
-In this part, we buid a people model to evaluate an employee in four
-aspects, in terms of \textbf{Quantitative Management Performance} ---
-work achievement, work ability, work attitude and potential. These
-four aspects are supposed to be quantized according to annual
-evaluation based on performance as judged by the supervisor and we
-take these independent variables as $A_{ac_i}$, $A_{ab_i}$, $A_{at_i}$
-and $A_{po_i}$ for each employee $i$. For each of the four parameters,
-it goes from 0 to 1. The statues are used for calculating the
-probability that employee can promote. Meanwhile, they influence
-leaving probability and team cohesiveness as well.
+In this part, we build an Employee Performance model to evaluate an employee in four
+aspects, in terms of Quantitative Management Performance ---
+work achievement, work ability, work attitude and potential\cite{3}. These
+four aspects are supposed to be quantized according to the annual
+evaluation based on performance judged by the supervisor and we
+take these independent variables as $A_{ac_i,t}$, $A_{ab_i,t}$, $A_{at_i,t}$
+and $A_{po_i,t}$ for each employee indexed by $i$. Each of these four parameters ranges from 0 to 1. They are used to calculate the
+promotion probability for each employee. Meanwhile, they influence the
+leaving probability and team cohesiveness.
 
-It is obvious that some of the parameters are somehow more important
-than others. So in an effort to make our model more accurate and
-reliable,we introduce a weighted index of deviation $AD_i$, with
+It is obvious that these parameters are of different importance. So in an effort to make our model more accurate and reliable, we introduce a weighted index of deviation $A_{i,t}$, with
 \begin{equation}
-  A_i=w_{ac} \cdot A_{ac_i} + w_{ab} \cdot A_{ab_i} + w_{at} \cdot A_{at_i} +
-  w_{po} \cdot A_{po_i}
+  A_{i,t}=w_{ac} \cdot A_{ac_i,t} + w_{ab} \cdot A_{ab_i,t} + w_{at} \cdot A_{at_i,t} +
+  w_{po} \cdot A_{po_i,t}
 \end{equation}
@@
 
-The meaning of the number in each cell is explained in Figure
-\ref{important}. The numbers themselves are based on our own
+The meaning of the number in each cell is explained in \textbf{Figure
+\ref{important}}\cite{11}. The numbers themselves are based on our own
 subjective decisions.
@@
   \begin{tabular}{cl}
-    \toprule{}
-    Intensity of Importance&Definition \\ \midrule{}
-    1                      &Equal Importance \\
-    2                      &Weak or slight \\
-    3                      &Moderate importance \\
-    4                      &Moderate plus \\
-    5                      &Strong importance \\
-    6                      &Strong plus \\
-    7                      &Very strong or demonstrated importance \\
-    8                      &Very, Very strong \\
-    9                      &Extreme importance \\ \bottomrule{}
+    \toprule[2pt]
+    Intensity of Importance & Definition \\ \midrule{}
+    &\\
+    1 & Equal Importance \\
+    2 & Weak or slight \\
+    3 & Moderate importance \\
+    4 & Moderate plus \\
+    5 & Strong importance \\
+    6 & Strong plus \\
+    7 & Very strong or demonstrated importance \\
+    8 & Very, Very strong \\
+    9 & Extreme importance \\ \bottomrule[2pt]
   \end{tabular}
@@
 
-We then get the weight of each factor by calculating the bigest
-eigenvalue and it's corresponding eigenvector, as given in Table \ref{weight}.
+We then get the weight of each parameter by calculating the bigest
+eigenvalue and it's corresponding eigenvector, as given in \textbf{Table \ref{weight}}.
 
@@
 \begin{center}
-\begin{tabular}{ccccc} \toprule{}
+\begin{tabular}{ccccc} \toprule[2pt]
   Factor  &$A_{ac}$    &$A_{ab}$   &$A_{at}$    &$A_{po}$\\ \midrule{}
-  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\ \bottomrule{}
+  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\ \bottomrule[2pt]
 \end{tabular}
@@
 We test the consistency of the preferences for this instance of the
-AHP.\@ For good consistency [Alonso and Lamata 2006, 446 - 447]:
+AHP.\@ For good consistency \cite{4}:
 
@@
 The social network model contains a directed weighted graph $G(V,E)$
-in which $V$ denote the employees and $E$ denote the connection
+in which $V$ denotes the employees and $E$ denotes the connection
 between employees. Since there are personnel changes, $G(V,E)$ will
@@
 
-First, we explain the way we build edges of $G_t(V_t,E_t)$.
+Firstly, we explain the way we build edges of $G_t(V_t,E_t)$.
 
@@
 office, since employees in the same division or office certainly know
-each other. So each division or office form a complete graph and
-employees in the differient division or office don't know others,
-which is impossible. To solve this problem, we build 10 edges for each
+each other. So each division or office form a complete graph. To establish inter-division or inter-office relations, we build 10 edges for each
 employee with employees in other divisions with equal
-probability. Then we build the other edges with probability
+probability. Then we build the other edges between employee indexed by
+$i$ and employee indexed by $j$ with the probability
 $p = \frac{\left|N_{i,t} \cap N_{j,t}\right|}{\left|N_{i,t} \cup
@@
 When $t > 0$, there will be employees leaving or joining the
-company. If an employee leave, all his edges with other employees with
-be deleted. If an employee newly join the company, he will follow
-steps which employees at $t = 0$ take. This is the dynamic process of
-graph $G_t(V_t,E_t)$.
+company. If an employee leaves, all his relations with other employees will
+be deleted. If an employee newly joins the company, he will follow
+steps which employees at $t = 0$ take.
 
-Let $s_{ij,t}$ denote the weight from $i$ to $j$ at time $t$. We have
-these properties of $G_t(V_t,E_t)$:
+Let $s_{ij,t}\in E_t$ denotes the weight from $i$ to $j$ in $t$-th
+month. We have these properties of $G_t(V_t,E_t)$:
 
@@
   consider another person his best friend while that person doesn't
-  consider him a good friend. This situation may appear because of the
-  relationship between superior and subordinate and the relationship
-  between person with more friend and person with less friend. In
+  consider him a good friend. This situation may appear in leader-member relations and the relations between person with more friend and person with less friend. In
   general, $s_{ij,t} \ne s_{ij,t}$ for the reason above.
@@
 
-  $a_{ij,t}$ denote the influence caused by the relationship between
-  superior and subordinate, $f_{ij,t}$ denote the influence caused by
-  the amount of friends for $i$ and $j$. We define
-$$a_{ij,t}=\begin{cases}
+  $a_{ij,t}$ denotes the influence caused by leader-member relation
+  between the employee indexed by $i$ and the employee indexed by $j$,
+  $f_{ij,t}$ denotes the influence calculated by the amount of friends
+  of the employee indexed by $i$ and the employee indexed by $j$. We define
+
+\begin{equation}
+a_{ij,t}=\begin{cases}
   \frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} \ge L_{j,t} \\
   1-\frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} < L_{j,t} \\
-\end{cases}$$
-, where $L_{i,t}$ denote the level of $i$ at time $t$, and
-$$f_{ij,t}=\frac{\left|N_{i,t} \cap
-    N_{j,t}\right|}{\left|N_{i,t}\right|}$$.
+\end{cases}
+\end{equation}
+
+, where $L_{i,t}$ denotes the level of $i$ in $t$-th month, and
+
+\begin{equation}
+f_{ij,t}=\frac{\left|N_{i,t} \cap
+    N_{j,t}\right|}{\left|N_{i,t}\right|}
+\end{equation}
 
@@
 
-First, we explain the model of promotion aimed to predict the
-promotion probability. We define the promotion rate of $i$ as
-$p_i$ to evaluate the probability to promote. As a matter of fact, if
-there is a vacancy, judging if an employee suits the site involves
-work experience and ability. It is essential that he is supposed to
-have several years of work experience according to issue 6. If an
-employee satisfies the experience condition, it turns out to think
-about his ability. Since in Human Performance Model, each employee's
-ability is evaluated by a parameter $A_{D_i}$. For each level of
-position, it has an ability standard, as shows in Table[]. The ability
-of an employee are supposed to reach the four standard parameters
-respectively, otherwise its $p_i$ is 0. For those who reach the
+Firstly, we explain the model of promotion designed to predict the
+promotion probability. The promotion rate of the employee indexed by $i$ is defined as
+$p_i$ to evaluate the probability of promotion. If
+there is a vacancy, judging if an employee is qualified for the
+position depends on his work experience and ability. First of all, it
+is essential to evaluate whether he has the special work
+experience. If he matches the condition of work experience, his
+ability will be evaluated subsequently. In Human Performance Model,
+each employee's
+ability is evaluated by a parameter $A_{D_i}$. Each level of
+position has its own ability standard. The ability
+of an employee is supposed to reach the four standard parameters
+respectively, otherwise its $p_i$ is set to 0. For those who reach the
 standard, the promotion probability can be calculated by the equation:
-$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ represent
-employee who have probability to promote.
+$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ represents
+employee who has probability to be promoted.
 
-According to assumption 1 and assumption 2, from $t$ to $t+1$, the
-model update once according to the following rules:
+According to \textbf{Assumption 1} and \textbf{Assumption 2}, the
+model updates monthly (from $t$ to $t+1$) obeying the following rules:
 
 \begin{itemize}
-\item [\textit{step 1}] Promotion: If there's a vacancy in superior
-  and $i$ has the ability to occupy this position, let $L_{i+1,t} =
-  L_{i,t}+1$ with probability mentioned above and build edges between
-  $i$ and his new colleagues.
-\item [\textit{step 2}] Churn: If $i$ isn't promoted, he will have the
-  probability to churn with a churn rate $l$.
-\item [\textit{step 3}] Stay: If $i$ hasn't been promoted or churned,
-  he will keep his job and do nothing.
-\item [\textit{step 4}] Recruit: Recruit for vacancies when all the
-  employees have done these 3 steps above.
+\item [\textit{step 1}] Promotion: If there's a superior vacancy
+  and the employee indexed by $i$ satisfies the requirement of the
+  position, let $L_{i+1,t} =
+  L_{i,t}+1$ with the probability mentioned above and build edges
+  between   $i$ and his new colleagues.
+\item [\textit{step 2}] Churn: If the employee indexed by $i$ isn't promoted, he will have the
+  probability to churn with a churn rate $l_{i,t}$.
+\item [\textit{step 3}] Stay: If the employee indexed by $i$ hasn't been promoted or churned,
+  he will be kept on his original position.
 \end{itemize}
@@
 \begin{itemize}
-\item \textbf{assumption 1} For the promotion probability and
+\item \textbf{Assumption 6} Except the promotion probability and
   organization change, the other factors effects the churn probability
-  is invariable.
+  are invariable.
 
-Though churn derives from varieties of reasons and they are actually
-lacking of known conditions and data to estimate them, we have to
-regard it as stable in our model.
+Though churn probability is influenced by varieties of factors, we do not  have enough information about these factors. Therefore, we have to
+regard most of them as constants in our model.
+
+\item \textbf{Assumption 7} Productivity of the company is the sum of the productivity of all employees.
+
 \end{itemize}
@@
 
-The network of the company we've built changes in terms of
-orgnizational churn and promotion. Considering various of factors in
-reality, we build an orgnizational churn and promotion model to
+The network of the company we've built changes from time to time due to
+organizational churn and promotion. Considering various of factors in
+reality, we build an organizational churn and promotion model to
 predict the dynamic process.
 
-The first part of the model is churn model.We define the churn rate of
-an employee $i$ as $l_i$ to evaluate the probability to churn. $l_i$ is
-usually controlled by sorts of factors to different degrees. We
-divides $l_i$ into three parts:$l_{i1}$, $l_{i2}$ and$l_{i3}$.  $l_{i1}$
-represents the churn rate because of lacking of promotion
-opportunity. $l_{i2}$ represents the churn rate because of the changes
-of other employees related to employee $i$. To simplify our model, we
-presume that $l_i1$, $l_i2$ is linear correlated with $(1-p_i)$ and
-$s_i$, which means
+The first part of the model is churn model. We define the churn rate of
+the employee indexed by $i$ as $l_{i,t}$. We divides $l_{i,t}$ into three
+parts: $l_{i1,t}$, $l_{i2,t}$ and $l_{i3,t}$.  $l_{i1,t}$
+represents the churn rate resulting from the lack of promotion
+opportunity. $l_{i2,t}$ represents the churn rate resulting from the personnel alterations of other employees who share an edge with employee indexed by $i$. To simplify our model, we
+presume that $l_{i1,t}$, $l_{i2,t}$ is linear correlated with $(1-p_{i,t})$ and
+$s_{ij,t}$, which means
 
 \begin{equation}
-  l_{i1}=\lambda_1(1-p_i),l_{i2}=\lambda_2s_i
+  l_{i1,t}=\lambda_1(1-p_{i,t}),l_{i2,t}=\lambda_2\sum_{j}s_{ij,t}
 \end{equation}
 
-$\lambda_1$ and $\lambda_2$ could be ensured in later calculation.
+$\lambda_1$ and $\lambda_2$ could be determined in later calculation.
 
-$l_{i3}$ represents the other factors we can't get any information from
-the known conditons so that we regard it as stable.  Thus
+$l_{i3,t}$ represents the other factors we regard as constants, about which we can't get enough information from the known conditons.  Thus
 
 \begin{equation}
-  l_i = \lambda_1(1-p_i) + \lambda_2s_i +l_i3
+l_{i,t}=\lambda_1(1-p_{i,t}) + \lambda_2 \sum_{j} s_{ij,t} + l_{i3,t}
 \end{equation}
 
-After analyzing a great deal of churn rate reports, we get the
-composition of the three parts are 10.9\%, 2.2\% and 75.4\%
-respectively. According to the percentage and the general
+After analyzing a great deal of churn rate reports, we define the
+coefficients of the three parts to 10.9\%, 2.2\% and 75.4\%
+respectively\cite{1}\cite{2}. With these percentages and the general
 churn rate 18\%, we can calculate $\lambda_1$, $\lambda_2$ and
-$l_{i3}$. As an orinigal condition,it satisfies
+$l_{i3,t}$. As an original condition, it satisfies
 
@@
 \begin{cases}
-  \lambda_1 \sum_{i=1}^{370}(1-p_i) & =10.9\% \times 370 \times 1.5\% \\
-  \lambda_2 \sum_{i=1}^{370}s_i & =2.2\% \times 370 \times 1.5\% \\
+  \lambda_1 \sum_{i=1}^{370}(1-p_{i,t}) & =10.9\% \times 370 \times 1.5\% \\
+  \lambda_2 \sum_{i=1}^{370}\sum_{j}s_{ij,t} & =2.2\% \times 370 \times 1.5\% \\
   l_{i3} & =1.5 \% \times 75.4 \%
@@
 
-Thus we can use Equation\ref{lambda} to calculate the churn rate $l_i$.
+Thus we can use \textbf{Equation \ref{lambda}} to calculate the churn rate $l_i$.
 
-Analyzing the consequence of this phenomenon, we use our program to
-simulate this process. As a result, we find a organizational churn in
-our simulation as shown in Figure \ref{organizational-churn}.
+To analyze the consequence of this phenomenon, we used our program to
+simulate this process. As a result, we observed an organizational churn in
+our simulation as shown in \textbf{Figure \ref{organizational-churn}}.
 
@@
 
-The black spots in the graph denote employees who have churned
+The black spots in the graph denote employees who have leaved during
+the past year. Each graph represents the status of 3 months after the
+privious graph. In the first 3 months, there is only one employee leaving the company. In the second 3 months, there are two employees leaving the
+company, while 4 more employees leave during the next 3 months. As a
+conclusion, there's a phenomenon of organizational churn according to
+our model.
 
@@
 
-First, we explain the concept of clustering coefficient [Duncan
-J. Watts and Steven Strogatz 1998] of $i$ denoted as $c_{i,t}$, which
+Firstly, we explain the concept of clustering coefficient [Duncan
+J. Watts and Steven Strogatz 1998] of employee indexed by $i$ denoted as $c_{i,t}$, which
 is a measure of the degree to which nodes in a graph tend to cluster
@@
 
-$$c_{i,t}=\dfrac{\left| \left\{ s_{jk,t}:v_j,v_k \in M_i,s_{jk,t} \in E
-    \right\} \right|}{k_{i,t}(k_{i,t}-1)}$$
+\begin{equation}
+c_{i,t}=\dfrac{\left| \left\{ s_{jk,t}:v_j,v_k \in M_i,s_{jk,t} \in E
+    \right\} \right|}{k_{i,t}(k_{i,t}-1)}
+\end{equation}
+
 where
@@
 
-\section{Performance and Analysis}
-\label{sec:performance-and-analysis}
+In order to get the definition of productivity, we give some factors
+that will influence productivity:
 
-\subsection{Analysis for Task 3}
-\label{sec:analysis-for-task-3}
+\begin{itemize}
+\item The first factor is churn rate which will reduce the
+  productivity if churn rate is at a high level.
+\item The second factor is the clustering coefficient $c_{i,t}$,
+  which determines team cohesiveness. We consider that the higher
+  $c_{i,t}$ is, the higher the productivity is.
+\item The third factor is the ability of employee indexed by $i$ mentioned in
+  \textbf{Section \ref{sec:human-model}}. It is obvious that a higher ability
+  brings a higher productivity.
+\item The fourth factor is the time duration that
+  $i$ stays in his position, denoted as $d_{i,t}$. Productivity will increase as the employee get familiar with his job.
+\item The last factor is the salary of employee indexed by $i$, denoed as
+  $salary_{i,t}$. It is obvious that salary will influence the productivity.
+\end{itemize}
 
-We assume that the company offers training programs for its employees monthly and newly hired employees start to get their salaries next month after they enter the company.
-With these two assumption, results can be drawn according to our model through simulation.
+According to the factors described above, we have the formula for calculating productivity:
 
-Budget can be divided into threee parts: salary budget, training budget and recruiting budget. The budget requirement predicted for next two years is listed in the table below in terms of $\sigma$.
+\begin{equation}
+  prod_{i,t}=salary_{i,t} \cdot c_{i,t} \cdot A_{i,t} \cdot d_{i,t} \cdot (1-l_{i,t})
+\end{equation}
 
-\begin{tabular}{*{4}{c}}\toprule[2pt]
-Total Budget & Salary Budget & Training Budget & Recruiting Budget\\ \midrule
-1170.8$\sigma$ & 951.387$\sigma$ & 164.423$\sigma$ & 55.08$\sigma$ \\ \bottomrule[2pt]
-\end{tabular}
+Finally, we introduce the direct and indirect effects on the
+organization's productivity. With the relation updates, edges in our
+employee network update, which causes the clustering coefficient
+changes. Meanwhile, the salary and work experience will change over
+time, which results in the changing of productivity. These factors
+effect the productivity collectively.
 
-\subsection{Analysis for Task 4}
-\label{sec:analysis-for-task-4}
+\section{Further Improved Model}
 
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=10cm]{task4_p.pdf}\\
-  \caption{Status of positions}\label{t4_p}
-\end{figure}
-
-To analyze the status of positions under different churn rate, we use
-our model to simulate dynamic processes with these churn rate
-constraints. We execute our program 100 times for each churn rate and
-average the predicted values. Figure \ref{t4_p} shows the averaged
-results our model predicted. Under all of these three conditions, the
-number of employees in the company keeps rising. The higher the churn
-rate, the lower the final full rate the company reaches after two
-years. But ICM can sustain its 80\% for positions even if the churn
-rate goes to 35\% according to our model's precition.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=10cm]{task4_r.pdf}\\
-  \caption{Recruiting budget}\label{t4_r}
-\end{figure}
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=7cm]{task4_t.pdf}
-  \includegraphics[width=7cm]{task4_s.pdf}\\
-  \caption{Training budget and salary budget}\label{t4_t_s}
-\end{figure}
-The churn rate effect the budget of the company as well. The three
-parts of the bugdet behave differently when churn rate increases. The
-calculated budget is shown in Figure \ref{t4_r} and Figure
-\ref{t4_t_s}. Each data point in three charts is an averaged result of
-10 predictions and a linear trendline is added to each chart. It is
-clear that recruiting budget showed in Figure \ref{t4_r} is likely to
-be proportional to the churn rate while salary budget and training
-budget showed in Figure \ref{t4_t_s} are likely to be inversely
-proportional to the churn rate.
-
-To maintain enough employees, the company has to spend more on
-recruiting. So high turnover rate directly increase the recruiting
-budget. High turnover rate's effect on training budget and salary
-budget is more complex. On the one hand, when churn rate goes up,
-vacancies in the middle level keeps rising due to long recruiting time
-and low promote rate. On the other hand, the vacancies in lower level
-remains low because of the short recruiting time. So the full rate of
-the company decreases when churn rate rises. Since training budget and
-salary budget are closely related to full rate, both of them decrease
-when turnover rate goes up.
-
-\subsection{Analysis for Task 5}
-\label{sec:analysis-for-task-5}
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=10cm]{task5_p.pdf}\\
-  \caption{Status of position}\label{t5_p}
-\end{figure}
-We apply following changes to our model to simulate the required process:\\
-\begin{itemize}
-\item Change the churn rate of junior managers and experienced supervisors to 30\%
-\item Prohit external recruiting
-\item Promoting only qualified employees
-\end{itemize}
-\begin{table}
-        \begin{center}
-                \begin{tabular}{l|cc}\toprule[2pt]
-                \bfseries Level of Position & \bfseries Modified & \bfseries Original\\ \midrule
-                Senior manager/Executive & 5.6 & 8.4\\
-                Junior manager/Executive & 9.0 & 18.4\\
-                Experienced supervisor & 7.4 & 23.0\\
-                Inexperienced supervisor & 9.2 & 23.2\\
-                Experienced employee & 72.6 & 107.4\\
-                Inexperienced employee & 99.6 & 149.6\\
-                Administrative clerk & 24.0 & 24.0\\ \bottomrule[2pt]
-                \end{tabular}
-                \caption{Status of position}\label{t5_p_t}
-        \end{center}
-\end{table}
-
-The result of simulation is shown in Figure \ref{t5_p} and Table
-\ref{t5_p_t}. All the data shown is an average of ten
-predictions. While the number of positions occupied remains stable
-with origial conditions, it drops remarkably with modified
-conditions.
-
-We list specific data of each level in Table \ref{t5_p_t}. In the
-modified case, the numbers of employees are lower than original case
-especially the those of middle levels. Since there is no external
-recruiting in modified case, it is obivious that the full rate will
-decrease due to employees' leave. Although some qualified employees
-can be promoted into higher level, the high churn rate of the middle
-level and difficulty of satisfying the promotion conditions make the
-numbers of middle level employees relatively low. The situation given
-in that task 5 will cause unrecoverable damage to ICM's HR
-health. With the full rate of middle level employees lower than 50\%,
-the HR structure is broken into fragments and the company won't be
-able to function normally.
-
-\section{Advice for HR}
-\label{sec:advice-for-hr}
-
-As the HR manager faces many problems such as identifying those that
+As the HR manager faces many problems such as identifying employees that
 are likely to churn and maximizing employees' knowledge and
-abilities, we explain our further improved model.
+abilities, we propose our further improved model to help the HR managers.
 
@@
 
-A worker is more likely to churn if he or she was connected to other
+An employee is more likely to churn if he or she was connected to other
 former employees who have churned. So there are two kinds of people
@@
 
-First, we should pay attention to those who have more friends than
+Firstly, we should pay attention to those who have more friends than
 others. Because of their wide connection with other employees, the
-consequence of their churn may be destructive, which cause many
+consequence of their churn may be destructive, which can cause many
 friends' churn.
 
-Second, we focus on those having more friends who have churned
+Secondly, we focus on those having more friends who have churned
 during the past year. This kind of people have a great probability to
@@
 
-We choose one sample in our simulations and 50 people in this sample
-to explain our incentive mechanism.
+We choose one sample in our simulations to explain our incentive
+mechanism. \textbf{Figure \ref{incentive-mechanism}} shows only 50
+people in the sample.
 
@@
   \includegraphics[width=7cm]{p2.eps}
-  \caption{employees should be pay attention
+  \caption{Employees should be pay attention
     to}\label{incentive-mechanism}
@@
 
-In Figure\ref{incentive-mechanism}, as we can see, each vertex
-represents an employee, each full line represents a relation between 2
-employees, each imaginary line represent an relation between person
-who is on the job and person who churn. There are 5
-employees in left graph we should pay attention to which are
-43, 97, 123, 265 and 301 because they have more full lines than
+In \textbf{Figure\ref{incentive-mechanism}}, as we can see, each vertex
+represents an employee, each solid line represents a relation between two
+employees, each dotted line represents an relation between a person
+who is on the job and a person who have churned. There are 5
+employees in left graph we should pay attention to which are employees indexed by 43, 97, 123, 265 and 301 because they have more solid lines than
 others. There are 6 employees in the right graph we should pay
-attention to which are 154, 175, 181, 182, 235 and 255 because they
-have more imaginary lines than others.
+attention to which are employees indexed by 154, 175, 181, 182, 235 and 255 because they
+have more dotted lines than others.
 
-We provide incentives to these employees which will decrease their
+We should provide incentives to these employees which will decrease their
 probabilities to churn.
 
-At time $t$, we choose top 10\% of the employees which have the
-properties above and decrease their churn rate by 50\%. As shown in
-Figure\ref{churn-rate}, the churn rate decrease rapidly.
+At $t$-th month, we choose top 10\% of the employees which have the
+properties above and reduce their churn rate by 50\%. As shown in
+\textbf{Table \ref{churn-rate}}, the churn rate decreases rapidly in one year.
 
-\begin{figure}[htb]
+\begin{table}[htb] 
   \centering
- % \includegraphics[width=11cm]{p4.pdf}
-  \caption{Churn rate-Time Curve}
+  \begin{tabular}{cllllllllllll}
+    \toprule[2pt]
+    t                          &1&2&3&4&5&6&7&8&9&10&11&12 \\
+    \midrule{}
+    without incentive mechanism&6&5&7&7&6&6&7&4&5&5&6&6 \\
+    with incentive mechanism   &5&3&4&4&4&5&3&3&4&2&4&3 \\
+  \bottomrule[2pt]
+  \end{tabular}
+  \caption{The amount of people leaving}
   \label{churn-rate}
-\end{figure}
+\end{table}
 
-\subsection{Matching Employees to the Right Position}
+\subsection{Matching Employees to the Right Positions}
 \label{sec:matching-employees-to-the-right-position}
 
-We consider different abilities of different employees. As we have an
+We assume that different employees have different abilities. As we have an
 annual evaluation based on performance for each employee and each
 division or office has it's necessarily needed abilities, we can match
-employees with their most suitable position.
+employees with their most suitable positions.
 
@@
 
-We reassign them once a year according to their
-evaluation. Figure\ref{reassign} shows productivity with reassignment
-and without reassignment. We can find that the productivity increase
-rapidly after reassign employees, which means reassignment truly help
-with productivity of the company.
+We reassign them annually according to their
+evaluation. \textbf{Figure \ref{reassign}} shows the productivity with reassignment
+and without reassignment. We can find that the productivity increases
+rapidly after reassigning employees, which means reassignment truly help
+with increasing the productivity of the company.
 
@@
 
-\section{Team Science}
+\section{Performance and Analysis}
+\label{sec:performance-and-analysis}
+
+\subsection{Analysis for Task 3}
+\label{sec:analysis-for-task-3}
+
+We assume that the company offers training programs for its employees monthly and newly hired employees start to get their salaries next month after they enter the company.
+With these two assumptions, results can be drawn according to our model through simulation.
+
+Budget can be divided into threee parts: salary budget, training budget and recruiting budget.
+The budget requirement predicted for next two years is listed in the \textbf{Table \ref{t3_t} }below in terms of $\sigma$.
+\\
+\begin{table}[htb]
+        \centering
+        \begin{tabular}{*{4}{c}}\toprule[2pt]
+        Total Budget & Salary Budget & Training Budget & Recruiting Budget\\ \midrule
+        1170.8$\sigma$ & 951.387$\sigma$ & 164.423$\sigma$ & 55.08$\sigma$ \\ \bottomrule[2pt]
+        \end{tabular}
+        \caption{Budget}\label{t3_t}
+\end{table}
+
+\subsection{Analysis for Task 4}
+\label{sec:analysis-for-task-4}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=10cm]{task4_p.pdf}\\
+  \caption{Status of positions}\label{t4_p}
+\end{figure}
+
+To analyze the status of positions under different churn rate, we use
+our model to simulate dynamic processes with these churn rate
+constraints. We execute our program 100 times for each churn rate and
+average the predicted values. \textbf{Figure \ref{t4_p}} shows the averaged
+results our model predicted. Under all of these three conditions, the
+number of employees in the company keeps rising. The higher the churn
+rate, the lower the final full rate the company reaches after two
+years. But ICM can sustain its 80\% for positions even if the churn
+rate goes to 35\% according to our model's prediction.
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=10cm]{task4_r.pdf}\\
+  \caption{Recruiting budget}\label{t4_r}
+\end{figure}
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=7cm]{task4_t.pdf}
+  \includegraphics[width=7cm]{task4_s.pdf}\\
+  \caption{Training budget and salary budget}\label{t4_t_s}
+\end{figure}
+The churn rate effects the budget of the company as well. Three
+parts of the bugdet behave differently when churn rate increases. The
+calculated budget is shown in \textbf{Figure \ref{t4_r}} and \textbf{Figure
+\ref{t4_t_s}}. Each data point in three charts is an averaged result of
+10 predictions and a linear trendline is added to each chart. It is
+clear that recruiting budget showed in \textbf{Figure \ref{t4_r}} is likely to
+be proportional to the churn rate while salary budget and training
+budget showed in \textbf{Figure \ref{t4_t_s}} are likely to be inversely
+proportional to the churn rate.
+
+To maintain enough employees, the company has to spend more on
+recruiting. So high turnover rate directly increase the recruiting
+budget. High turnover rate's effect on training budget and salary
+budget is more complex. On the one hand, when churn rate goes up,
+vacancies in the middle level keeps rising due to long recruiting time
+and low promotion rate. On the other hand, the vacancies in lower level
+rises due to the huge base number. So the full rate of
+the company decreases when churn rate rises. Since training budget and
+salary budget are closely related to full rate, both of them decrease
+when turnover rate goes up.
+
+\subsection{Analysis for Task 5}
+\label{sec:analysis-for-task-5}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=10cm]{task5_p.pdf}\\
+  \caption{Status of position}\label{t5_p}
+\end{figure}
+We apply following changes to our model to simulate the required process:\\
+\begin{itemize}
+\item Change the churn rate of junior managers and experienced supervisors to 30\%
+\item Prohibit external recruiting
+\item Promoting only qualified employees
+\end{itemize}
+\begin{table}
+        \begin{center}
+                \begin{tabular}{lcc}\toprule[2pt]
+                \bfseries Level of Position & \bfseries Modified & \bfseries Original\\ \midrule
+                Senior manager/Executive & 5.6 & 8.4\\
+                Junior manager/Executive & 9.0 & 18.4\\
+                Experienced supervisor & 7.4 & 23.0\\
+                Inexperienced supervisor & 9.2 & 23.2\\
+                Experienced employee & 72.6 & 107.4\\
+                Inexperienced employee & 99.6 & 149.6\\
+                Administrative clerk & 24.0 & 24.0\\ \bottomrule[2pt]
+                \end{tabular}
+                \caption{Status of position}\label{t5_p_t}
+        \end{center}
+\end{table}
+
+The result of simulation is shown in \textbf{Figure \ref{t5_p}} and \textbf{Table
+\ref{t5_p_t}}. All the data shown is an average of ten
+predictions. While the number of positions occupied remains stable
+with origial conditions, it drops remarkably with modified
+conditions.
+
+We list specific data of each level in \textbf{Table \ref{t5_p_t}}. In the
+modified case, the numbers of employees are lower than original case
+especially those of the middle levels. Since there is no external
+recruiting in modified case, it is obivious that the full rate will
+decrease due to employees' leave. Although some qualified employees
+can be promoted into higher level, the high churn rate of the middle
+level and difficulty of satisfying the promotion conditions make the
+numbers of middle level employees relatively low. The situation given
+in task 5 will cause unrecoverable damage to ICM's HR
+health. With the full rate of middle level employees lower than 50\%,
+the HR structure is broken into fragments and the company won't be
+able to function normally.
+
+\section{Team Science and Multi-layered Network}
 \label{sec:team-science}
+This part summarizes the potential use of team science and multi-layered networks in this problem.
 
-This part shows how our model connects to other organizational network
-layers such as information flow, trust, influence, and
+Team Science shows how team works with team and how team members
+intereffect. The theory is helpful for promoting team cohesiveness and
+teamwork effeciency. The existing researches suggest that an
+organization aiming to improve its teamwork effeciency should establish its team
+cognition, evaluate the individuals appropriately, provide team
+training and try to identify the factors that influence the team performance\cite{8}\cite{9}.
+
+A well-designed model can be great helpful to achieve goals listed above. Multi-layered model is a good example. We will introduce how to connect our model to the other organizational network
+layers such as information flow, trust, influence and
 friendship. Number the layers from 0 to
@@
 
-Still, in each network layer $G_\alpha$, $N_i$ represents emploee
+Still, in each network layer $G_\alpha$, $N_i$ represents employee
 $i$. The edge $e_{ij}$ connects between two nodes $N_i$ and
@@
 connect these network layers together to built a general network
-$G_e=(V, E, C)$, V is node set, C is color set, $E \subset  V\times
-V\times C$ is edge set. In the general model, different layers effects
-each other. Take for example, if the friendship between employee $i$
-and employee $j$ is deeper, with other conditions the same,their
-information flow is more fluent. $w_{ij}^\alpha$ is changing with time
+$G_e=(V, E, C)$, V is node set, C is color set, $E\subset V\times
+V\times C$ is edge set\cite{10}. In the general model, different layers effect
+each other. Take an example, if the friendship between employee indexed by $i$
+and employee indexed by $j$ is deeper, with other conditions same, their
+information flow will be more fluent. $w_{ij}^\alpha$ is changing with time
 flows and $G_e$ is a dynamic network.
 
-However, human capital network make the maily effect on other network
-layers. In the general network, if an empolyee churns or is
+However, the human capital network plays a leading role to other network layers. In the general network, if an empolyee churns or is
 reassigned, the edge related to him will change. That is,
@@
 
-a
+We analyze sensitivity of our model by running the program with modified parameters. The results are shown in \textbf{Table \ref{sensi}}.
+\begin{table}[htb]
+\begin{tabular}{cccccccc}\toprule[2pt]
+\thead{Parameter}    &\thead{Variation}           &\thead{N}                    &\thead{p}             &\thead{Training\\ Budget}       &   \thead{Salary\\ Budget}   &  \thead{Recruit\\ Budget}     &\thead{Total\\ Budget}     \\
+\hline r & +5\%        &0\%                  & +1.3\%       &+0.46\% &+0.6\% & -0.49\% &+0.5\%     \\
+                    & -5\%        &+0.8\%               & -4\%         &-3.5\%  &-4.4\% & -8.5\%  &+4.5\%     \\
+\hline c   & +5\%        &-1.4\%               & -2.1\%       &-0.2\%  &-0.5\% &+12.4\%  &+0.1\%    \\
+                    & -5\%        &0\%                  & +1.1\%       &0.4\%   &+0.7\% &-11.7\%  &+0.1\%    \\
+\hline ra        & +1          &-0.9\%               & -0.6\%       &-1.2\%  &-1.7\% &+24.0\%  &-0.5\%   \\
+                    & -1          &+1.1\%               & +6.7\%       &+1.0\%  &+0.8\% &-17.4\%  &-0.1\%      \\ \bottomrule[2pt]
+\end{tabular}
+\caption{Sensitivity analysis}\label{sensi}
+\end{table}
+
+With $c$ rising, $N$ and $p$ keeps stable. When $c$ drops, they varies
+more clearly. It is because in current condition, the positions are
+nearly all occupied. It won't make obvious change if $c$ rises. For
+the similar reason, $N$ and $p$ changes little when $c$ drops while
+they changes more clearly when $c$ increases. If $ra$ drops to 1, $N$
+and $p$ increase considerably, which proves that reducing middle
+manangers' churn rate is quite beneficial to HR health. As for the budget
+requirements, training budget, salary budget and total budget stay
+stable, while recruiting budget changes quite obviously. It is because
+the change of these paramenters greatly changed the number of the
+newly-recruited employees. The other budgets change relatively lower
+because they are mainly associated to $N$, which doesn't change much
+while $ra$ varies.
 
@@
 \begin{itemize}
-\item Our model make fully use of the theory of multilayer networks so
+\item Our model make full use of the theory of multilayer networks so
   that it quantizes the relation accurately and reasonablly.
 \item Our model exellently proves the interaction among these
-  factors:leave probability, promotion probability and productivity.
-\item The network we built include both microcosmic part and
-  macrocosmic part, and they react to each other.
-\item Our model proves the effection of time.
+  factors: leave probability, promotion probability and productivity.
+\item The network we built includes both microcosmic and macrocosmic which react to each other.
+\item Our model is robust according to sensitivity test.
 \end{itemize}
@@
 \begin{itemize}
-\item Limited by the time,we neglected sorts of factors which are not so significant.In fact, the model still has space to be perfected.
-\item The result has some randomness.
+\item Limited by the time, we neglected sorts of factors which are not
+  so significant. In fact, the model still has space to be perfected.
+\item Our result involves some randomness.
 \end{itemize}
@@
 
-a
+For Task 1, we propose an Employee Relation Model based on the SNA
+(social network analysis) technique. Meanwhile each node (employee) in
+the network has several characteristics which are used to evaluate the
+employee corresponding to the node. We calculate the grade of each
+employee by evaluating based on AHP (analytic hierarchy process)
+technique. Based on these grades, we predict the promotion probability
+for each employee in the company.
+
+For Task 2, we establish an Organizational Churn Model to simulate the
+effects caused by the leaving of employees. Furthermore, we introduce
+a new method to calculate the productivity considering five factors,
+including churn rate, team cohesiveness, employee ability, work
+experience and salary.
+
+For Task 3 and 4, we calculate the budget for the next two years and
+analyze the influence of different churn rates. Our data show that the
+cost of recruitment increases, while the cost of training and salary
+decreases when the churn rate rises.
+
+For Task 5, we simulate the situation which doesn't have external
+recruitment, and get the result that the amount of employees decreases
+rapidly.
+
+For Task 6, we discuss the potential usage of team science and
+multi-layered network and apply them into our model.
+
+Moreover, we propose an improved version of our model which can
+analyze the influence of reassignment and provide reference value to
+HR managers for incentive mechanism.
 
@@
 
-\bibitem{} Huang Y. A Study of the Performance Assessment of State-owned Power Enterprisees[D]. Tianjing University, 2010.
+\bibitem{1} Huang Y. A Study of the Performance Assessment of State-owned Power Enterprisees[D]. Tianjing University, 2010.
 
-\bibitem{} Journal T E D O T. The Investigation Report of the Condition of employee churn in 2011[J]. China New Time, 2012(2).
+\bibitem{2} Journal T E D O T. The Investigation Report of the Condition of employee churn in 2011[J]. China New Time, 2012(2).
 
-\bibitem{} Zhang J. The Empirical Research of the Factors effecting employee churn in Resource-oriented Enterprise in Yuncheng,Shandong [D]. Southerneast University, 2014.
+\bibitem{3} Zhang J. The Empirical Research of the Factors effecting employee churn in Resource-oriented Enterprise in Yuncheng,Shandong [D]. Southerneast University, 2014.
 
-\bibitem{} MEJNewman. The Structure and Function of Complex Networks[D]. University of Michigan, 2003.
+\bibitem{4} J.A.Alonso and M.T.Lamata, Consistency in the Analytic Hierarchy Process: A New Approach, International Journal of Uncertainty, Fuzziness and Knowledge-Based Systems, Vol.14, No.4, 2006.
 
-\bibitem{} Fang J, Zheng Z, Bi Q, etal. A Brand-new
+\bibitem{5} MEJNewman. The Structure and Function of Complex Networks[D]. University of Michigan, 2003.
+
+\bibitem{6} Fang J, Zheng Z, Bi Q, etal. A Brand-new
 Interdisciplinary Science: Network Science (Part One)[J]. Progress in Physics, 2007, 27(3).
 
-\bibitem{} Fang J, Zheng Z, Bi Q, etal. A Brand-new
+\bibitem{7} Fang J, Zheng Z, Bi Q, etal. A Brand-new
 Interdisciplinary Science: Network Science (Part Two)[J]. Progress in Physics, 2007, 27(4).
+
+\bibitem{8} E.
+Salas, N.J.
+Cooke, and M.A.
+Rosen.
+(2008).
+On Teams, Teamwork, and Team Performance: Discoveries and Developments.
+Human Factors: The Journal of the Human Factors and Ergonomics Society June 2008 vol.
+50 no.
+3540-547.
+
+\bibitem{9} D. Stokols, K.L. Hall, B.K. Taylor, R.P. Moser (2008). The Science of Team Science: Overview of the Field and Introduction to the Supplement, Am J Prev Med 2008;35(2S): S77-S89.
+
+\bibitem{10} Mikko Kivelä, Alexandre Arenas, Marc Barthelemy, James P.
+Gleeson, Yamir Moreno, Mason A.
+Porter.
+(2013).
+Multilayer Networks, J.
+Complex Networks, 2(3): 203-271 (2014); arXiv preprint arXiv:1309.7233, 2013.
+
+\bibitem{11} Saaty, Thomas L. Decision making with the analytic hierarchy process. International Journal of Service Sciences. 2008, 1: 83–98.
 

### 2015-02-09 Pro-C/Algo_1.cpp
Add c++ program

@@ -1,0 +1,778 @@
+#include<cstdlib>
+#include<cstdio>
+#include<cstring>
+#include<string>
+#include<iostream>
+#include<vector>
+#include<list>
+#include<ctime>
+#include<math.h>
+//#include<ctime>
+using namespace std;
+const int lim[]={10,20,25,25,110,150,30};
+const int limm[]={8,14,15,15,104,142,24};
+const double farrelation=1.0/5.0;
+const double baseSkill[7][4]={{0.7,0.7,0.8,0.8},
+							  {0.6,0.6,0.7,0.7},
+							  {0.6,0.6,0.5,0.5},
+							  {0.5,0.5,0.5,0.5},
+							  {0.5,0.5,0.4,0.4},
+							  {0.4,0.4,0.4,0.4},
+							  {0.5,0.5,0.4,0.4}};
+const double levelPos[7]={7,6,5,4,3,1,2};
+const double levelPd[7]={8,4,2,1.5,1,0.9,0.9};
+const double levelRc[7]={1.2,0.7,0.6,0.6,0.3,0.1,0.3};
+const double levelTr[7]={0.5,0.6,0.2,0.3,0.1,0.3,0.05};
+double PPP=0.65;
+double lambda_1=0.00549545,lambda_2=0.000604455;
+double sPD[50],sBDR[50],sBDT[50],sBDS[50],sRR[50];
+int js=0;
+double pd[380];
+struct _Block;
+struct _People;
+struct _Level;
+struct _Level{
+};
+struct _People{
+	int id;
+	int level;
+	double skill[4];
+	double time;
+	double lpd,npd;
+	_Block *block;
+	_People(int level):level(level){
+		time=rand()*1.0/RAND_MAX;
+	}
+}*People[400];
+struct _Block{
+	int id;
+	int levelcount[10];
+	double skill[4];
+	_People *employe[10][15];
+	string name;
+	_Block(string name,int level[]):name(string(name)){
+		for (int i=0;i<7;i++)
+			levelcount[i]=level[i];
+		memset(employe,0,sizeof(employe));
+	}
+	//levelcount SM JM S IS E IE A 
+}*Block[50];
+
+vector< pair<_People**,_Block*> > Level[10];
+vector<int> tree[50];
+list<int> l;
+int disT[50][50];
+int bTree[50][50];
+int ubTree[50][50];
[…]

### 2015-02-09 Pro-C/nparse.py

@@ -1,0 +1,53 @@
+import json
+flink=open('2Pythonlink')
+fnode=open('2Pythonnode')
+fbjs=open('2Pythonbjs')
+fout=open('nout.json',"w")
+lim=15
+njs=-1
+ndic={}
+nxjs={}
+nbjs={}
+ans={"nodes":[],"links":[]}
+for line in fnode:
+	word=line.strip().split()
+	njs=njs+1
+	ndic[int(word[0])]=njs
+	nxjs[int(word[0])]=0
+	ans["nodes"].append({"name":word[0]+'_'+word[1],"group":int(word[2])})
+for line in fbjs:
+	word=line.strip().split()
+	nbjs[word[0]]=int(word[1])
+for i in ans["nodes"]:
+	i["degree"]=nbjs[i["name"].split('_')[0]]
+for line in flink:
+	word=line.strip().split()
+	s=int(word[0])
+	t=int(word[1])
+	if (ndic[s]>lim) and (ndic[t]>lim):
+		continue;
+	if (ndic[s]<=lim) and (ndic[t]<=lim):
+		continue;
+	if (ndic[s]<=lim):
+		nxjs[t]=nxjs[t]+1
+	if (ndic[t]<=lim):
+		nxjs[s]=nxjs[s]+1	
+flink.close()
+flink=open('2Pythonlink')
+for line in flink:
+	word=line.strip().split()
+	s=int(word[0])
+	t=int(word[1])
+	if (nxjs[t]==0) and (nxjs[s]==0):
+		continue
+	ans["links"].append({"source":ndic[s],"target":ndic[t],"value":int(word[2]),"xors":(ndic[s]>lim) and (ndic[t]>lim)})
+for i in ans["nodes"]:
+	i["xdegree"]=nxjs[int(i["name"].split('_')[0])]
+encodedjson = json.dumps(ans)
+print(encodedjson,file=fout)
+
+
+fout.close()
+
+
+   # {"source":8,"target":0,"value":2},

### 2015-02-09 Pro-C/parse.py

@@ -1,0 +1,32 @@
+import json
+flink=open('2Pythonlink')
+fnode=open('2Pythonnode')
+fbjs=open('2Pythonbjs')
+fout=open('out.json',"w")
+njs=-1
+ndic={}
+nbjs={}
+ans={"nodes":[],"links":[]}
+for line in fnode:
+	word=line.strip().split()
+	njs=njs+1
+	ndic[int(word[0])]=njs
+	ans["nodes"].append({"name":word[0]+'_'+word[1],"group":int(word[2])})
+for line in fbjs:
+	word=line.strip().split()
+	nbjs[word[0]]=int(word[1])
+for i in ans["nodes"]:
+	i["degree"]=nbjs[i["name"].split('_')[0]]
+for line in flink:
+	word=line.strip().split()
+	s=int(word[0])
+	t=int(word[1])
+	ans["links"].append({"source":ndic[s],"target":ndic[t],"value":int(word[2])})
+encodedjson = json.dumps(ans)
+print(encodedjson,file=fout)
+
+
+fout.close()
+
+
+   # {"source":8,"target":0,"value":2},

### 2015-02-09 Pro-C/parse4task2.py

@@ -1,0 +1,35 @@
+import json
+flink=open('2Pythonlink')
+fnode=open('2Pythonnode')
+fbjs=open('2Pythonbjs')
+fout=open('outts2.json',"w")
+njs=-1
+ndic={}
+nbjs={}
+ans={"nodes":[],"links":[]}
+for line in fnode:
+	word=line.strip().split()
+	if (int(word[1])!=30):
+		continue
+	njs=njs+1
+	ndic[int(word[0])]=njs
+	ans["nodes"].append({"name":word[0]+'_'+word[1],"group":int(word[2])})
+for line in fbjs:
+	word=line.strip().split()
+	nbjs[word[0]]=int(word[1])
+for i in ans["nodes"]:
+	i["degree"]=nbjs[i["name"].split('_')[0]]
+for line in flink:
+	word=line.strip().split()
+	s=int(word[0])
+	t=int(word[1])
+	if (s in ndic) and (t in ndic):
+		ans["links"].append({"source":ndic[s],"target":ndic[t],"value":int(word[2])})
+encodedjson = json.dumps(ans)
+print(encodedjson,file=fout)
+
+
+fout.close()
+
+
+   # {"source":8,"target":0,"value":2},
